### 2021-01-24 article/Untitled.Rnw
adding article

\documentclass[article]{jss}
\usepackage{thumbpdf,lmodern}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.25in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{eqparbox}
%% new custom commands
\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
\SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@
\raggedbottom
\graphicspath{ {./images/} }
\renewcommand{\algorithmiccomment}[1]{\hfill\eqparbox{COMMENT}{\# #1}}
\makeatletter
\newcommand{\distas}[1]{\mathbin{\overset{#1}{\kern\z@\sim}}}%
\newsavebox{\mybox}\newsavebox{\mysim}
\newcommand{\distras}[1]{%
  \savebox{\mybox}{\hbox{\kern3pt$\scriptstyle#1$\kern3pt}}%
  \savebox{\mysim}{\hbox{$\sim$}}%
  \mathbin{\overset{#1}{\kern\z@\resizebox{\wd\mybox}{\ht\mysim}{$\sim$}}}%
}
\makeatother

\author{Eric Weine\\University of Chicago
   \And Mary Sara McPeek\\University of Chicago}
\Plainauthor{Eric Weine, Mary Sara McPeek}

\title{Efficient Calculation of Improved Simultaneous Testing Bands for QQplots}
%\author{Eric Weine and Mary Sara McPeek}
\Abstract{
Quantile-Quantile plots (QQplots) are often difficult to interpret because it is unclear how large the deviation from the theoretical distribution must be to indicate a lack of fit. Current packages and algorithms towards this end either do not ensure a robust Type I error rate, are too slow, or are under-powered to deviations in the tails of the distribution. In this paper, we present an efficient algorithm that computes simultaneous testing bands for QQplots. These bands have a variety of desirable properties, including being fast to compute and being equally sensitive to deviations in all parts of the null distribution, including the tails.
}

\Keywords{QQplots, Equal Local Levels, Kolmolgorov-Smirnov, GWAS, Multiple Testing}

\Address{
  Mary Sara McPeek\\
  Department of Statistics\\
  University of Chicago\\
  924 E 57th St., Chicago, IL\\
  E-mail: \email{mcpeek@uchicago.edu}\\
  URL: \url{https://galton.uchicago.edu/~mcpeek/}
}
\begin{document}

\maketitle

\section{Introduction}
Quantile-Quantile plots (QQplots) are a common statistical tool used to judge if a sample comes from a specified distribution \citep{wilk_gnanadesikan_1968}. Despite their ubiquity, they are often difficult to interpret because it is challenging to determine if the magnitude of the deviation from the specified distribution is large enough to indicate a lack of fit as opposed to sampling variance. To make this determination, it is useful to put testing bands on a QQplot.
\newline
\newline
A number of methods have been created towards this end. First, some available software puts pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic \citep{qqplotr}. This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified distribution. Second, the Komolgorov-Smirnov (KS) test is a common method for creating joint bands \citep{kolmogoroff1941confidence, smirnov1944approximate}. While this method ensures the correct Type I error by using the distribution of the KS statistic, this test suffers from very low power under a variety of reasonable alternatives \citep{aldor2013power}. In the same work, Aldor-Noiman et al. introduced a much more powerful test (under most alternatives) called the Tail Sensitive (TS) test. This test uses simulation to conduct an $\eta$ level test on each order statistic such that the overall test has an $\alpha$ level Type I error. This test has a variety of desirable properties, but because it requires simulation it is extremely slow in large datasets.
\newline
\newline
In what follows, we present a method that yields the same results as the TS test but does so substantially faster because of an efficient recursive calculation. We then demonstrate this test on a few multiple testing scenarios including Type I error calibration and genetic studies.
\section{Methods}

\subsection{Local Levels For Global Null Hypothesis Testing}

Suppose we have observations

\begin{equation*}
  X_{1}, ..., X_{n} \distras{iid} F,
\end{equation*}
and we are interested in conducting the following hypothesis test

\begin{equation*}
      H_{0}: F = F_{0} \textrm{ vs. } H_{A}: F \neq F_{0}
\end{equation*}
with level $\alpha$, where all parameters of $F_{0}$ are known. One approach to this problem, referred to as ``local levels,'' is to conduct separate hypothesis tests on each of the order statistics $X_{(i)}$, where each test has Type I error rate $\eta_{i}$ \citep{gontscharuk2016goodness}. Then, we reject the global null hypothesis if at least one of the $n$ tests results in a rejection. That is, we construct a set of intervals

\begin{equation*}
    (h_{1}, g_{1}), ..., (h_{n}, g_{n}),
\end{equation*}
and we reject $H_{0}$ if for any $i$

\begin{equation*}
    X_{(i)} \not\in (h_{i}, g_{i}).
\end{equation*}
If we know the local level $\eta_{i}$, then
\begin{equation}
    h_{i} = F^{-1}_{i}(\eta_{i} / 2) \text{ and } g_{i} = F^{-1}_{i}(1 - \eta_{i} / 2),
\end{equation}
where $F_{i}$ is the CDF of the $i^{th}$ order statistic. Thus, the difficulty is in determining an appropriate vector of local levels $(\eta_{1}, ..., \eta_{n})$ for which the resulting global level is $\alpha$. In our case, we want to create testing bands that are ``agnostic'' to any alternative distribution. By this, we mean that we would like to design a test that applies equal scrutiny to each order statistic, and thus we set
% an alternative explanation is that we're trying to design a test that would have optimum power under the alternative distribution where the probability of any of the order statistics being outside of the pointwise null region is equal.
\begin{equation}
    \eta_{1} = \eta_{2} = ... = \eta_{n} = \eta.
\end{equation}

This is known as ``equal local levels.''
\newline
\newline
\noindent Given the sample size $n$ and the desired level $\alpha$ we present the following algorithm for obtaining $\eta$ in two steps:
\newline
\newline
1. Given a proposed testing region $(h_{1}, g_{1}), ..., (h_{n}, g_{n})$, where $h_{i} < g_{i}$ for $i = 1, ..., n$, find the probability of $X_{(1)}, ..., X_{(n)}$ falling outside of this region under the null.
\newline
\newline
2. Using the algorithm described in step 1, conduct a binary search on the space of the local level $\eta$. This involves proposing a value of $\eta$, calculating the corresponding region $(h_{1}, g_{1}), ..., (h_{n}, g_{n})$ using equation (1), and then using step 1 to check if the region achieves the desired global Type I error rate $\alpha$.
\newline
\newline
We now describe these two steps in more detail:
\newline
\newline
\textbf{Step 1:} First, note that under the null hypothesis,

\begin{equation*}
    F_{0}(X_{1}), ..., F_{0}(X_{n}) \distras{iid} U(0, 1).
\end{equation*}
Thus, without loss of generality, we can build the algorithm for step 1 assuming that

\begin{equation*}
    X_{1}, ..., X_{n} \distras{iid} U(0, 1)
\end{equation*}
% I'll worry about the uncertainty in parameter estimates later
% I'll probably want some sort of a diagram here eventually
We are trying to calculate the following probability
\begin{equation*}
    \alpha = P_{0}\Big(\bigcup\limits_{i=1}^{n} X_{(i)} \notin (h_{i}, g_{i})\Big)
\end{equation*}
Where $P_{0}$ is the probability under the null hypothesis. It is easier to calculate this as
\begin{equation*}
    \alpha = 1 - P_{0}\Big(\bigcap\limits_{i=1}^{n} X_{(i)} \in (h_{i}, g_{i})\Big)
\end{equation*}
\newline
To calculate this value, it is easier to transform the events over order statistics to multinomial events. To do this, we introduce the following notation:
\newline
\newline
Let $b_{1}, ..., b_{2n}$ be the sorted values of $h_{1}, ..., h_{n}, g_{1}, ..., g_{n}$ in ascending order. We also define $b_{0} = 0$ and $b_{2n + 1} = 1$. We will divide the interval $(b_{0}, b_{2n + 1})$ into $2n + 1$ bins, where bin 1 is $(b_{0}, b_{1})$, bin 2 is $(b_{1}, b_{2}), ...,$ and bin $2n + 1$ is $(b_{2n}, b_{2n + 1})$. Note that because the uniform distribution is continuous, the probabilities associated with the endpoints of the bins are 0, so it does not matter if the left and right boundaries of these intervals are open or closed. Let $N_{j} = \sum_{i = 1}^{n}\mathds{1}\Big(X_{i} \in (b_{j - 1}, b_{j})\Big)$ denote the random variable that counts the number of X's falling into bin j, for $1 \leq j \leq 2n+1$, and let $S_{k} =  \sum_{j=1}^{k} N_{j}$ be the $kth$ partial sum of the $N$'s, for $1 \leq k \leq 2n+1$. The key to the algorithm is that the following two events are the same:
\begin{equation*}
    \{X_{(i)} \in (h_{i}, g_{i}) \text{ for } i = 1, ..., n\} = \{l_{k} \leq S_{k} \leq u_{k} \textrm{ for } k = 1, 2, ..., 2n\},
\end{equation*}
where

\begin{align*}
u_{k} &=
    \begin{cases}
      0, & \text{if}\ k=1 \\
      \sum_{i = 1}^{k - 1} \mathds{1} \big(b_{i} \in \{h_{1}, ..., h_{n}\}\big), & \text{otherwise}
    \end{cases}\\
    l_{k} &=
      \sum_{i = 1}^{k} \mathds{1} \big(b_{i} \in \{g_{1}, ..., g_{n}\}\big)
\end{align*}
(See Figure 1 above for intuition).
% I should give some intuition here with a diagram or a better explanation
\begin{figure}
\centering
\begin{tikzpicture}
\draw (0,0) --(12.5,0);
\draw (0,-.5) --(0,.5);
\node at (0,.75) {0};
\draw (12.5,-.5) --(12.5,.5);
\node at (12.5,.75) {1};
\draw (1.5,-.5) --(1.5,.5);
\node at (1.5,.75) {h1};
\draw (5.25,-.5) --(5.25,.5);
\node at (5.25,.75) {g1};
\draw (9,-.5) --(9,.5);
\node at (9,.75) {h3};
\draw (3.5,-.5) --(3.5,.5);
\node at (3.5,.75) {h2};
\draw (7.25,-.5) --(7.25,.5);
\node at (7.25,.75) {g2};
\draw (11,-.5) --(11,.5);
\node at (11,.75) {g3};
\node at (.75,.25) {$u_{1} = 0$};
\node at (.75,-.25) {$l_{1} = 0$};
\node at (2.5,.25) {$u_{2} = 1$};
\node at (2.5,-.25) {$l_{2} = 0$};
\node at (4.35,.25) {$u_{3} = 2$};
\node at (4.35,-.25) {$l_{3} = 1$};
\node at (6.25,.25) {$u_{4} = 2$};
\node at (6.25,-.25) {$l_{4} = 2$};
\node at (8.15,.25) {$u_{5} = 2$};
\node at (8.15,-.25) {$l_{5} = 2$};
\node at (10,.25) {$u_{6} = 3$};
\node at (10,-.25) {$l_{6} = 3$};
\end{tikzpicture}
\caption{Example of how $l_{k}$ and $u_{k}$, $k = 1, ..., 2n$, depend on the relative positions of $h_{1}, ..., h_{n}$ and $g_{1}, ..., g_{n}$, for a case with n = 3. }
\end{figure}
Finally, we define
\begin{equation*}
    c_{w}^{(k)} = P_{0}(S_{k} = w \textrm{ and } l_{j} \leq S_{j} \leq u_{j} \textrm{ for } j = 1, ..., k - 1), \textrm{for } k = 1, ..., 2n \textrm{ and } w = 1, ..., n.
\end{equation*}
Our basic approach to step 1 is a recursive calculation of these $c_{w}^{(k)}$ values. Then, the global level $\alpha$ could be computed as $1 - c_{n}^{(2n)}$ in the general case. However, for the special case in which $(h_{1}, g_{1}), ..., (h_{n}, g_{n})$ are derived from equal local levels, i.e. equation (2) holds, then as a result of the symmetry in the problem, we need only calculate $c_{w}^{(k)}$ for $k = 1, ..., n+1$ instead of $k = 1, ... , 2n$. This shortcut is implemented below in the pseudocode for step 1. The algorithm calculates the probability of a valid allocation (under the null hypothesis) of points in bins by looping over each bin and making a recursive calculation.
% In this algorithm I think that I want to introduce Mary Sara's calculation. I should maybe introduce some notation before this, but I think that it's probably fine.
\begin{algorithm}[H]
\caption{Calculate Type I error $\alpha$ from proposed rejection region}
\textbf{Input:} Vector of lower bound values $(h_{1}, ..., h_{n})$, vector of upper bound values $(g_{1}, ..., g_{n})$, where we require $h_{i} < g_{i}$ for $i = 1, ..., n$.
\newline
\textit{get\_level\_from\_bounds\_two\_sided}$(h_{1}, ..., h_{n}, g_{1}, ..., g_{n})$
\begin{algorithmic}[1]
\STATE $b_{1}, ..., b_{2n} \leftarrow \textbf{sort}(h_{1}, ..., h_{n}, g_{1}, ..., g_{n})$
\STATE {$c_{0}^{(1)} \leftarrow (1 - b_{1})^{n}$}
\STATE $l_{k} \leftarrow 0$
\STATE $u_{k} \leftarrow 0$
\FOR{$k = 2, ..., n + 1$}
\IF{$b_{k - 1} \in \{h_{1}, ..., h_{n}\}$}
\STATE $u_{k} \leftarrow u_{k - 1} + 1$
\ENDIF
\IF{$b_{k} \in \{g_{1}, ..., g_{n}\}$}
\STATE $l_{k} \leftarrow l_{k - 1} + 1$
\ENDIF
\FOR{$j = l_{k}, ..., u_{k}$}
\STATE $c_{j}^{(k)} \leftarrow 0 $
\FOR{$m = l_{k - 1}, ..., min(u_{k - 1}, j)$}
\STATE $c_{j}^{(k)} \leftarrow  c_{j}^{(k)} + c_{m}^{(k - 1)} * dbinom(x = j - m, size = n-m, prob = \frac{(b_{k} - b_{k - 1})}{(1 - b_{k - 1})})$
\ENDFOR
\ENDFOR
\ENDFOR
\STATE $1 - \alpha \leftarrow 0$
\FOR{$l = l_{n}, ..., u_{n}$}
\STATE $1 - \alpha \leftarrow 1 - \alpha + \frac{c_{l}^{(n)} * c_{n - l}^{(n + 1)}}{dbinom(x = l, size = n, prob = b_{n})}$
\ENDFOR
\RETURN $\alpha$
\end{algorithmic}
\textbf{end}
\end{algorithm}
Now, we derive the algorithm. \textbf{Initialization:} (Lines 2 through 4 of Algorithm 1)
\begin{align*}
    c_{0}^{(1)} &= P_{0}(S_{1} = 0)\\
    &= P_{0}\Big(\bigcap\limits_{i=1}^{n}\{X_{i} \in (b_{1}, 1)\}\Big)\\
    &= \prod\limits_{i=1}^{n}P_{0}\Big(X_{i} \in (b_{1}, 1)\Big) &\textrm{(by independence)}\\
    &= (1 - b_{1})^{n} &\textrm{(Since each $X_{i} \sim~ U(0, 1)$ under the null)}
\end{align*}
Also, we initialize $l_{1} = 0$ and $u_{1} = 0$ because the only allowable partial sum is 0 in the first bin.
\textbf{Recursion:} (Line 15 of Algorithm 1)
\begin{flalign*}
    \indent\indent c_{j}^{(k)} &= P_{0}(S_{k} = j \textrm{ and } l_{q} \leq S_{q} \leq u_{q} \textrm{ for } q = 1, ..., k - 1)\\
    &= P_{0}\Big(\bigcup\limits_{m=l_{k- 1}}^{min(j, u_{k- 1})} \{S_{k - 1} = m \textrm{ and } N_{k} = j - m \textrm{ and } l_{q} \leq S_{q} \leq u_{q} \textrm{ for } q = 1, ..., k - 2\}\Big)\\
    &= \sum\limits_{m=l_{k- 1}}^{min(j, u_{k- 1})}P_{0}(S_{k - 1} = m \textrm{ and } N_{k} = j - m \textrm{ and } l_{q} \leq S_{q} \leq u_{q} \textrm{ for } q = 1, ..., k - 2)\\
    &= \sum\limits_{m=l_{k- 1}}^{min(j, u_{k- 1})}P_{0}(S_{k - 1} = m \textrm{ and } l_{q} \leq S_{q} \leq u_{q} \textrm{ for } q = 1, ..., k - 2)*\\
    &P_{0}(N_{k} = j - m | S_{k - 1} = m \textrm{ and } l_{q} \leq S_{q} \leq u_{q} \textrm{ for } q = 1, ..., k - 2)\\
    &= \sum\limits_{m=l_{k- 1}}^{min(j, u_{k- 1})}c_{m}^{(k - 1)} * P_{0}(N_{k} = j - m | S_{k - 1} = m)\\
    &= \sum\limits_{m=l_{k- 1}}^{min(j, u_{k- 1})}c_{m}^{(k - 1)} * P(B = j - m), \textrm{where }B \sim Binomial\left(n - m, \frac{b_{k} - b_{k - 1}}{1 - b_{k - 1}}\right),
    &&
\end{flalign*}
\newline
\indent\indent which is easily computed.
\newline
\newline
As noted above, in the general case, we could use this recursion to obtain $c_{n}^{(2n)}$, and then compute $\alpha = 1 - c_{n}^{(2n)}$. However, in the special case of equal local levels, we can use symmetry to speed the calculation by only computing the $c_{w}^{(k)}$ values for $k = 1, ..., n+1$ and $w = 1, ..., n$, and performing the calculation on line 21 of Algorithm 1, as we now demonstrate. First, we define the following values:
\begin{align*}
\Tilde{u}_{k} &=
    \begin{cases}
      0, & \text{if}\ k = 2n \\
      \sum_{i = k + 1}^{2n} \mathds{1} \big(b_{i} \in \{g_{1}, ..., g_{n}\}\big), & \text{otherwise}
    \end{cases}\\
    \Tilde{l}_{k} &=
      \sum_{i = k}^{2n} \mathds{1} \big(b_{i} \in \{h_{1}, ..., h_{n}\}\big)\\
    T_{k} &= \sum_{j = k + 1}^{2n + 1}N_{j} = n - S_{k}
\end{align*}
Now, we make the following observations:
\newline
\newline
(1) With equal local levels, $g_{i} = 1 - h_{n + 1 - i}$ for $i = 1, ..., n$ since $F_{Beta(i, n + 1 - i)}^{-1}(1 - \frac{\eta}{2})$ = $1 - F_{Beta(n + 1 - i, i)}^{-1}(\frac{\eta}{2})$.
\newline
\newline
(2) $b_{k} = 1 - b_{2n + 1 - k}$ for $k = 1, ..., 2n$ by (1). 
\newline
\newline
(3) $u_{k} = \Tilde{u}_{2n + 1 - k}$ and $l_{k} = \Tilde{l}_{2n + 1 - k}$, for $k = 1,..., 2n$ by (1) and (2).
\newline
\newline
(4) The random vector $(N_{1}, ..., N_{k})$ has the same distribution as $(N_{2n + 1}, ..., N_{2n+2-k})$ for $k = 1, ..., 2n + 1$. This follows from the fact that the vector $(X_{1}, ..., X_{n})$ has the same distribution as $(1 - X_{1}, ..., 1 - X_{n})$ (since each $X_{i}$ is independent uniform) and (2).
\newline
\newline
(5) The random vector $(S_{1}, ..., S_{k})$ has the same distribution as $(T_{2n}, ..., T_{2n + 1 - k})$ for $k = 1, ..., 2n$. This follows from (4). 
\newline
\newline
(6)
\begin{align*}
    c_{j}^{(k)} &= P_{0}(S_{k} = j \textrm{ and } l_{q} \leq S_{q} \leq u_{q} \textrm{ for } q = 1, ..., k - 1)\\
    &= P_{0}(T_{2n + 1 - k} = j \textrm{ and } \Tilde{l}_{r} \leq T_{r} \leq \Tilde{u}_{r} \textrm{ for } r = 2n + 2 - k, ..., 2n).\\
\end{align*}
This follows from (3) and (5). 
\newline
\newline
(7) Conditional on $S_{k}$, the random vector $(X_{(S_{k} + 1)}, ..., X_{(n)})$ is distributed as the order statistics of $n - S_{k}$ $U(b_{k}, 1)$ independent random variables.
\newline
\newline
(8) The random vector $(S_{1}, ..., S_{r})$ and the random vector $(T_{r}, ..., T_{n})$ are independent conditional on $S_{r}$. This follows directly from (7).
\newline
\newline
Combining the above results, we can write
\begin{equation*}
    \{X_{(i)} \in (h_{i}, g_{i}) \textrm{ for } i = 1,..., n\} = \{l_{k} \leq S_{k} \leq u_{k} \textrm{ for } k = 1, ..., 2n\}
\end{equation*}
Also, observe that for any $2 \leq r \leq 2n - 1$, we have
\begin{equation*}
    \{l_{k} \leq S_{k} \leq u_{k} \textrm{ for } k = 1, ..., 2n\} = 
\end{equation*}
\begin{equation*}
    \{l_{k} \leq S_{k} \leq u_{k} \textrm{ for } k = 1, ..., r \textrm{ and } T_{r} = n - S_{r} \textrm{ and } \Tilde{l}_{k} \leq T_{q} \leq \Tilde{u}_{k} \textrm{ for } q = r, ..., 2n\}
\end{equation*}
Thus, we can write 
\begin{align*}
    \sum_{j = l_{r}}^{u_{r}} &P(S_{r} = j \textrm{ and } l_{k} \leq S_{k} \leq u_{k} \textrm{ for } k = 1, ..., r - 1)\\
    &\cdot I(\Tilde{l}_{r} \leq n - j \leq \Tilde{u}_{r})
    \cdot P(\Tilde{l}_{q} \leq T_{q} \leq \Tilde{u}_{r} \textrm{ for } q = r + 1,..., 2n | T_{r} = n - j)\\
    &= \sum_{j = l_{r}}^{u_{r}} c_{j}^{(r)} \cdot I(\Tilde{l}_{r} \leq n - j \leq \Tilde{u}_{r}) \cdot P(\Tilde{l}_{q} \leq T_{q} \leq \Tilde{u}_{r} \textrm{ for } q = r + 1,..., 2n | T_{r} = n - j) \\
    &= \sum_{j = l_{r}}^{u_{r}} c_{j}^{(r)} \cdot I(\Tilde{l}_{r} \leq n - j \leq \Tilde{u}_{r}) \cdot \frac{P(\Tilde{l}_{q} \leq T_{q} \leq \Tilde{u}_{r} \textrm{ for } q = r + 1,..., 2n \textrm{ and } T_{r} = n - j)}{T_{r} = n - j} \\
    &= \sum_{j = l_{r}}^{u_{r}} c_{j}^{(r)} \cdot \frac{c_{n - j}^{(2n + 1 - r)}}{\binom{n}{j}b_{r}^{j}(1 - b_{r})^{n-j}}
\end{align*}
Now, if we let $r = n$ above, then we get 
\begin{equation*}
    P_{0}\Big(\bigcap\limits_{i=1}^{n} X_{(i)} \in (h_{i}, g_{i})\Big) = \sum_{j = l_{n}}^{u_{n}} c_{j}^{(n)} \cdot \frac{c_{n - j}^{(n + 1)}}{\binom{n}{j}b_{n}^{j}(1 - b_{n})^{n-j}}
\end{equation*}
which is line 21 in the psuedo-code above.
\newline
\newline
Empirically, it seems that our algorithm has computational complexity $O(n^{2})$. For a dense grid of values of $n$ between $10$ and $50,000$, the number of recursive steps required (line 15 in algorithm 1 above) scales with $n^{2}$. More precisely, it appears that the number of recursive steps required is very close to $8n^{2}$. While each recursive step itself requires calculating a binomial probability which is $O((n + 1)!)$ due to the calculation of the binomial coefficient multiplied by a quantity with powers as large as $n$, these calculations can be memoized with $O(n^{2})$ cost. Thus, these binomial probability calculations do not change the big $O$ complexity of the algorithm.
\newline
\newline
% The step below should definitely be put in an algorithm float as well. I need to make sure all of this makes sense before I finish it, but afterh this the discussion and the abstract should be relatively easy to follow through on and complete.
\textbf{Step 2:} This step is done with a simple binary search over $\eta$. We begin by setting $\eta_{upper} = \frac{-log(1 - \alpha)}{(2 * log(log(n)) * log(n))}$ since this is an upper bound on the local level as shown by Gontscharuk et al., and we set $\eta_{lower} = \frac{\alpha}{n}$, as this is the lower bound given by the Bonferroni correction. The pseudocode is shown below:
\begin{algorithm}[H]
\caption{Calculate testing bounds from global level $\alpha$ and sample size $n$}
\textbf{Input:} Local level $\alpha$, sample size $n$, tolerance $\epsilon$
\newline
\textit{get\_bounds\_two\_sided}$(\alpha, n, \epsilon)$
\begin{algorithmic}[1]
\STATE $\eta_{upper} \leftarrow \frac{-log(1 - \alpha)}{(2 * log(log(n)) * log(n))}$
\STATE $\eta_{lower} \leftarrow \frac{\alpha}{n}$
\STATE $\alpha_{mid} \leftarrow \infty$
\WHILE{$\frac{\alpha_{mid} - \alpha}{\alpha} > \epsilon$}
\STATE $\eta_{mid} \leftarrow \frac{\eta_{upper} + \eta_{lower}}{2}$
\STATE $h_{1}, ..., h_{n} \leftarrow qbeta(p = \frac{\eta_{mid}}{2}$, shape1 = c(1:n), shape2 = c(n:1))
\STATE $g_{1}, ..., g_{n} \leftarrow qbeta(p = 1 - \frac{\eta_{mid}}{2}$, shape1 = c(1:n), shape2 = c(n:1))
\STATE $\alpha_{mid} \leftarrow get\_level\_from\_bounds\_two\_sided(h_{1}, ..., h_{n}, g_{1}, ..., g_{n})$
\ENDWHILE
\RETURN $h_{1}, ..., h_{n}, g_{1}, ..., g_{n}$
\end{algorithmic}
\textbf{end}
\end{algorithm}
\section{Local Level Approximations in Large Samples}
For sufficiently large values of the number of tests $n$, it can be expedient to apply an accurate asymptotic approximation of the local level $\eta$ corresponding to global level $\alpha$ in place of exact computation. Previously, Gontscharuk and Finner showed that the asymptotic local level for global level $\alpha$ and number of tests $n$ is
\begin{equation*}
    \eta_{asymp} = \frac{log(1 - \alpha)}{2log(log(n))log(n)}
\end{equation*}
\citep{gontscharuk2017asymptotics}. However, as they note, this approximation gives poor performance for $n$ even as large as $10^{4}$. To improve this approximation, they propose to add a smaller order correction term, resulting in an approximation of the form
\begin{equation}
    \eta_{approx} = \frac{log(1 - \alpha)}{2log(log(n))log(n)}\left[1 - c_{\alpha}\frac{log(log(log(n)))}{log(log(n))}\right],
\end{equation}
where $c_{\alpha}$ is chosen empirically. For the values $\alpha = .01, .05, \textrm{ and } .1$ they chose $c_{\alpha} = 1.6, 1.3, \textrm{ and } 1.1$, respectively. To select these $c_{\alpha}$ values, the authors calculated the values of $\eta$ to high precision on a grid of values up until $n = 10,000$. To further test these approximations, we decided to calculate the values of $\eta$ with high precision on a grid of values up to $n = 500,000$ for $\alpha = .01, .05$. Based on our evaluation, we found that $c_{\alpha} = 1.3$ is satisfactory for $\alpha = .05$, but that $c_{\alpha} = 1.6$ for $\alpha = .01$ was not sufficiently accurate for our purposes (see Figure 2).
\begin{figure}
\begin{center}
    \includegraphics{images/c_alpha_1_6.png}
    \includegraphics{images/c_alpha_1_591.png}
\end{center}
\caption{Relative Error of Local Level vs. Number of Tests for $\eta_{approx}$ for $\alpha = .01$ with $c_{\alpha} = 1.6$ (top) $c_{\alpha} = 1.591$ (bottom).}
\end{figure}
This approximation begins anti-conservative for small values of $n$, becomes very accurate for values of $n$ around 2,500, and then becomes and remains substantially conservative for even very large values of $n$. 
\newline
\newline
In addition to implementing algorithms 1 and 2, which, in principle, can be applied for any $n$ and $\alpha$, our package offers a faster approximate approach specifically for $\alpha = .01 \textrm{ and } .05$. For smaller values of $n$, up to $100,000$, we have pre-calculated values of $\eta$ on a dense grid of values of $n$. If the user inputs a value of $n$ less than or equal to $100,000$, we either return back the pre-computed value of $\eta$ if $n$ happens to be a grid point, or we use linear interpolation if the value of $n$ is between grid points, which leads to a highly accurate approximation. If the user inputs a value of $n$ greater than $100,000$, we use the asymptotic approximation given in (3), but with $c_{\alpha} = 1.591 \textrm{ and } 1.3$ for $\alpha = .01 \textrm{ and } .05$, respectively. We found that $c_{\alpha} = 1.591$ led to much better performance for $\alpha = .01$ for large values of $n$, as can be seen in Figure 2. Our package also implements the approximation given in equation (3) for $\alpha = .1$ with $c_{\alpha} = 1.1$, but we did not pre-compute any grid for these values due to limited computational resources.
\section{Examples}
As noted above, the algorithm presented is only correct if all of the parameters of $F_{0}$ are known, and all $X_{1}, ..., X_{n}$ are independent. While both of these assumptions may only hold in a small number of cases, the methods above are still useful in a variety of scenarios.
\newline
\newline
One of the main advantages of the local levels method, is that it can easily be used to put testing bands onto QQplots by simply graphing each $(h_{i}, g_{i})$ interval. This allows us to examine how a dataset might deviate from some null distribution much better than simply applying a test that yields a binary conclusion. Below, we present a few examples where a QQplot is useful, and where the local levels test seems ideal for assessing deviation from a global null hypothesis.

\subsection{Examining the P-value Distribution for Testing Procedures}

% It may also make sense for me to make a comparison to the Kolmogorov-Smirnov statistic at some point. I should probably include some instructive graphs or something.
% I want to have a different paragraph to better introduce the concept
% This shouldn't be too difficult
Suppose we have devised a new testing procedure to test a null hypothesis $H_{0}$ with test statistic $T(X_{1}, ..., X_{n})$, and we wish to establish that this test has correct Type I error rate.
\newline
\newline
Typically, the verification of Type I error rate is done using the following procedure:
\newline
\newline
(1) Generate $m$ simulated datasets: $(X_{1}^{(1)}, ..., X_{n}^{(1)}), ..., (X_{1}^{(m)}, ..., X_{n}^{(m)})$ under $H_{0}$.
\newline
\newline
(2) Apply the test $T$ to each of these datasets at level $\alpha$ to yield $m$ reject / not-reject conclusions: $c_{1}, ..., c_{m}$, where $c_{i} = 1$ if $H_{0}$ is rejected and $0$ otherwise.
\newline
\newline
(3) Conduct a test to confirm that the mean of $c_{1}, ..., c_{m}$ is $\alpha$.
\newline
\newline
While the above procedure provides reliable information about the Type I error calibration for one level of $\alpha$, it provides little information about the global calibration of p-values. Instead, we suggest the following procedure:
\newline
\newline
(1) As above.
\newline
\newline
(2) Apply the test $T$ to each of these datasets to yield $m$ p-values: $p_{1}, ..., p_{m}$.
\newline
\newline
(3) Apply the local levels procedure to test if $p_{1}, ..., p_{m} \distras{iid} U(0, 1)$.
% It seems to me that this would be an opportune time to make a comparison to the KS-test, but I'm not totally sure.
% I should maybe put some graphs here as well.
\newline
\newline
This allows us to easily visualize the global calibration of the p-values with just one graph and diagnose any issues if they exist. In Step 3, one could use many different testing bands. However, in the calibration of p-values, we typically don't have the expectation that our p-values would be more likely to deviate from uniform in some regions than others, and so it makes sense to use the local levels test because it is agnostic to the alternative distribution. Moreover, since it is generally most concerning if p-values are not calibrated in the lower tail of the distribution, the local levels test is preferable to the standard KS test because it is much more sensitive in the tails (Aldor-Noiman 2013).

\subsubsection{Chi-Square Test for Independence in a \texorpdfstring{$2 \times 2$}{2 X 2} Table}

\bibliography{refs}
\end{document}

### 2021-01-24 article/article.tex
adding article

\documentclass[article]{jss}

%% -- LaTeX packages and custom commands ---------------------------------------

%% recommended packages
\usepackage{thumbpdf,lmodern}

%% another package (only for this demo article)
\usepackage{framed}

%% new custom commands
\newcommand{\class}[1]{`\code{#1}'}
\newcommand{\fct}[1]{\code{#1()}}

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}

%% -- Article metainformation (author, title, ...) -----------------------------

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Achim Zeileis\\Universit\"at Innsbruck
   \And Second Author\\Plus Affiliation}
\Plainauthor{Achim Zeileis, Second Author}

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A Short Demo Article: Regression Models for Count Data in \proglang{R}}
\Plaintitle{A Short Demo Article: Regression Models for Count Data in R}
\Shorttitle{A Short Demo Article in \proglang{R}}

%% - \Abstract{} almost as usual
\Abstract{
  This short article illustrates how to write a manuscript for the
  \emph{Journal of Statistical Software} (JSS) using its {\LaTeX} style files.
  Generally, we ask to follow JSS's style guide and FAQs precisely. Also,
  it is recommended to keep the {\LaTeX} code as simple as possible,
  i.e., avoid inclusion of packages/commands that are not necessary.
  For outlining the typical structure of a JSS article some brief text snippets
  are employed that have been inspired by \cite{Zeileis+Kleiber+Jackman:2008},
  discussing count data regression in \proglang{R}. Editorial comments and
  instructions are marked by vertical bars.
}

%% - \Keywords{} with LaTeX markup, at least one required
%% - \Plainkeywords{} without LaTeX markup (if necessary)
%% - Should be comma-separated and in sentence case.
\Keywords{JSS, style guide, comma-separated, not capitalized, \proglang{R}}
\Plainkeywords{JSS, style guide, comma-separated, not capitalized, R}

%% - \Address{} of at least one author
%% - May contain multiple affiliations for each author
%%   (in extra lines, separated by \emph{and}\\).
%% - May contain multiple authors for the same affiliation
%%   (in the same first line, separated by comma).
\Address{
  Achim Zeileis\\
  Journal of Statistical Software\\
  \emph{and}\\
  Department of Statistics\\
  Faculty of Economics and Statistics\\
  Universit\"at Innsbruck\\
  Universit\"atsstr.~15\\
  6020 Innsbruck, Austria\\
  E-mail: \email{Achim.Zeileis@R-project.org}\\
  URL: \url{https://eeecon.uibk.ac.at/~zeileis/}
}

\begin{document}

%% -- Introduction -------------------------------------------------------------

%% - In principle "as usual".
%% - But should typically have some discussion of both _software_ and _methods_.
%% - Use \proglang{}, \pkg{}, and \code{} markup throughout the manuscript.
%% - If such markup is in (sub)section titles, a plain text version has to be
%%   added as well.
%% - All software mentioned should be properly \cite-d.
%% - All abbreviations should be introduced.
%% - Unless the expansions of abbreviations are proper names (like "Journal
%%   of Statistical Software" above) they should be in sentence case (like
%%   "generalized linear models" below).

\section[Introduction: Count data regression in R]{Introduction: Count data regression in \proglang{R}} \label{sec:intro}

\begin{leftbar}
The introduction is in principle ``as usual''. However, it should usually embed
both the implemented \emph{methods} and the \emph{software} into the respective
relevant literature. For the latter both competing and complementary software
should be discussed (within the same software environment and beyond), bringing
out relative (dis)advantages. All software mentioned should be properly
\verb|\cite{}|d. (See also Appendix~\ref{app:bibtex} for more details on
\textsc{Bib}{\TeX}.)

For writing about software JSS requires authors to use the markup
\verb|\proglang{}| (programming languages and large programmable systems),
\verb|\pkg{}| (software packages), \verb|\code{}| (functions, commands,
arguments, etc.). If there is such markup in (sub)section titles (as above), a
plain text version has to be provided in the {\LaTeX} command as well. Below we
also illustrate how abbrevations should be introduced and citation commands can
be employed. See the {\LaTeX} code for more details.
\end{leftbar}

Modeling count variables is a common task in economics and the social sciences.
The classical Poisson regression model for count data is often of limited use in
these disciplines because empirical count data sets typically exhibit
overdispersion and/or an excess number of zeros. The former issue can be
addressed by extending  the plain Poisson regression model in various
directions: e.g., using sandwich covariances or estimating an additional
dispersion parameter (in a so-called quasi-Poisson model). Another more formal
way is to use a negative binomial (NB) regression. All of these models belong to
the family of generalized linear models (GLMs). However, although these models
typically can capture overdispersion rather well, they are in many applications
not sufficient for  modeling excess zeros. Since \cite{Mullahy:1986} there is
increased interest in zero-augmented models that address this issue by a second
model component capturing zero counts. An overview of count data models in
econometrics, including  hurdle and zero-inflated models, is provided in
\cite{Cameron+Trivedi:2013}.

In \proglang{R} \citep{R}, GLMs are provided by the model fitting functions
\fct{glm} in the \pkg{stats} package and \fct{glm.nb} in the \pkg{MASS} package
\citep[][Chapter~7.4]{Venables+Ripley:2002} along with associated methods for
diagnostics and inference. The manuscript that this document is based on
\citep{Zeileis+Kleiber+Jackman:2008} then introduced hurdle and zero-inflated
count models in the functions \fct{hurdle} and \fct{zeroinfl} in the \pkg{pscl}
package \citep{Jackman:2015}. Of course, much more software could be discussed
here, including (but not limited to) generalized additive models for count data
as available in the \proglang{R} packages \pkg{mgcv} \cite{Wood:2006}, 
\pkg{gamlss} \citep{Stasinopoulos+Rigby:2007}, or \pkg{VGAM} \citep{Yee:2009}.

%% -- Manuscript ---------------------------------------------------------------

%% - In principle "as usual" again.
%% - When using equations (e.g., {equation}, {eqnarray}, {align}, etc.
%%   avoid empty lines before and after the equation (which would signal a new
%%   paragraph.
%% - When describing longer chunks of code that are _not_ meant for execution
%%   (e.g., a function synopsis or list of arguments), the environment {Code}
%%   is recommended. Alternatively, a plain {verbatim} can also be used.
%%   (For executed code see the next section.)

\section{Models and software} \label{sec:models}

The basic Poisson regression model for count data is a special case of the GLM
framework \cite{McCullagh+Nelder:1989}. It describes the dependence of a count
response variable $y_i$ ($i = 1, \dots, n$) by assuming a Poisson distribution
$y_i \sim \mathrm{Pois}(\mu_i)$. The dependence of the conditional mean
$\E[y_i \, | \, x_i] = \mu_i$ on the regressors $x_i$ is then specified via a
log link and a linear predictor
%
\begin{equation} \label{eq:mean}
\log(\mu_i) \quad = \quad x_i^\top \beta,
\end{equation}
%
where the regression coefficients $\beta$ are estimated by maximum likelihood
(ML) using the iterative weighted least squares (IWLS) algorithm.

\begin{leftbar}
Note that around the \verb|{equation}| above there should be no spaces (avoided
in the {\LaTeX} code by \verb|%| lines) so that ``normal'' spacing is used and
not a new paragraph started.
\end{leftbar}

\proglang{R} provides a very flexible implementation of the general GLM
framework in the function \fct{glm} \citep{Chambers+Hastie:1992} in the
\pkg{stats} package. Its most important arguments are
\begin{Code}
glm(formula, data, subset, na.action, weights, offset,
  family = gaussian, start = NULL, control = glm.control(...),
  model = TRUE, y = TRUE, x = FALSE, ...)
\end{Code}
where \code{formula} plus \code{data} is the now standard way of specifying
regression relationships in \proglang{R}/\proglang{S} introduced in
\cite{Chambers+Hastie:1992}. The remaining arguments in the first line
(\code{subset}, \code{na.action}, \code{weights}, and \code{offset}) are also
standard  for setting up formula-based regression models in
\proglang{R}/\proglang{S}. The arguments in the second line control aspects
specific to GLMs while the arguments in the last line specify which components
are returned in the fitted model object (of class \class{glm} which inherits
from \class{lm}). For further arguments to \fct{glm} (including alternative
specifications of starting values) see \code{?glm}. For estimating a Poisson
model \code{family = poisson} has to be specified.

\begin{leftbar}
As the synopsis above is a code listing that is not meant to be executed,
one can use either the dedicated \verb|{Code}| environment or a simple
\verb|{verbatim}| environment for this. Again, spaces before and after should be
avoided.

Finally, there might be a reference to a \verb|{table}| such as
Table~\ref{tab:overview}. Usually, these are placed at the top of the page
(\verb|[t!]|), centered (\verb|\centering|), with a caption below the table,
column headers and captions in sentence style, and if possible avoiding vertical
lines.
\end{leftbar}

\begin{table}[t!]
\centering
\begin{tabular}{lllp{7.4cm}}
\hline
Type           & Distribution & Method   & Description \\ \hline
GLM            & Poisson      & ML       & Poisson regression: classical GLM,
                                           estimated by maximum likelihood (ML) \\
               &              & Quasi    & ``Quasi-Poisson regression'':
                                           same mean function, estimated by
                                           quasi-ML (QML) or equivalently
                                           generalized estimating equations (GEE),
                                           inference adjustment via estimated
                                           dispersion parameter \\
               &              & Adjusted & ``Adjusted Poisson regression'':
                                           same mean function, estimated by
                                           QML/GEE, inference adjustment via
                                           sandwich covariances\\
               & NB           & ML       & NB regression: extended GLM,
                                           estimated by ML including additional
                                           shape parameter \\ \hline
Zero-augmented & Poisson      & ML       & Zero-inflated Poisson (ZIP),
                                           hurdle Poisson \\
               & NB           & ML       & Zero-inflated NB (ZINB),
                                           hurdle NB \\ \hline
\end{tabular}
\caption{\label{tab:overview} Overview of various count regression models. The
table is usually placed at the top of the page (\texttt{[t!]}), centered
(\texttt{centering}), has a caption below the table, column headers and captions
are in sentence style, and if possible vertical lines should be avoided.}
\end{table}

%% -- Illustrations ------------------------------------------------------------

%% - Virtually all JSS manuscripts list source code along with the generated
%%   output. The style files provide dedicated environments for this.
%% - In R, the environments {Sinput} and {Soutput} - as produced by Sweave() or
%%   or knitr using the render_sweave() hook - are used (without the need to
%%   load Sweave.sty).
%% - Equivalently, {CodeInput} and {CodeOutput} can be used.
%% - The code input should use "the usual" command prompt in the respective
%%   software system.
%% - For R code, the prompt "R> " should be used with "+  " as the
%%   continuation prompt.
%% - Comments within the code chunks should be avoided - these should be made
%%   within the regular LaTeX text.

\section{Illustrations} \label{sec:illustrations}

For a simple illustration of basic Poisson and NB count regression the
\code{quine} data from the \pkg{MASS} package is used. This provides the number
of \code{Days} that children were absent from school in Australia in a
particular year, along with several covariates that can be employed as regressors.
The data can be loaded by
%
\begin{Schunk}
\begin{Sinput}
R> data("quine", package = "MASS")
\end{Sinput}
\end{Schunk}
%
and a basic frequency distribution of the response variable is displayed in
Figure~\ref{fig:quine}.

\begin{leftbar}
For code input and output, the style files provide dedicated environments.
Either the ``agnostic'' \verb|{CodeInput}| and \verb|{CodeOutput}| can be used
or, equivalently, the environments \verb|{Sinput}| and \verb|{Soutput}| as
produced by \fct{Sweave} or \pkg{knitr} when using the \code{render_sweave()}
hook. Please make sure that all code is properly spaced, e.g., using
\code{y = a + b * x} and \emph{not} \code{y=a+b*x}. Moreover, code input should
use ``the usual'' command prompt in the respective software system. For
\proglang{R} code, the prompt \code{"R> "} should be used with \code{"+  "} as
the continuation prompt. Generally, comments within the code chunks should be
avoided -- and made in the regular {\LaTeX} text instead. Finally, empty lines
before and after code input/output should be avoided (see above).
\end{leftbar}

\begin{figure}[t!]
\centering
\includegraphics{article-visualization}
\caption{\label{fig:quine} Frequency distribution for number of days absent
from school.}
\end{figure}

As a first model for the \code{quine} data, we fit the basic Poisson regression
model. (Note that JSS prefers when the second line of code is indented by two
spaces.)
%
\begin{Schunk}
\begin{Sinput}
R> m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine,
+    family = poisson)
\end{Sinput}
\end{Schunk}
%
To account for potential overdispersion we also consider a negative binomial
GLM.
%
\begin{Schunk}
\begin{Sinput}
R> library("MASS")
R> m_nbin <- glm.nb(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine)
\end{Sinput}
\end{Schunk}
%
In a comparison with the BIC the latter model is clearly preferred.
%
\begin{Schunk}
\begin{Sinput}
R> BIC(m_pois, m_nbin)
\end{Sinput}
\begin{Soutput}
       df      BIC
m_pois 18 2046.851
m_nbin 19 1157.235
\end{Soutput}
\end{Schunk}
%
Hence, the full summary of that model is shown below.
%
\begin{Schunk}
\begin{Sinput}
R> summary(m_nbin)
\end{Sinput}
\begin{Soutput}
Call:
glm.nb(formula = Days ~ (Eth + Sex + Age + Lrn)^2, data = quine, 
    init.theta = 1.60364105, link = log)

Deviance Residuals: 
    Min       1Q   Median       3Q      Max  
-3.0857  -0.8306  -0.2620   0.4282   2.0898

Coefficients: (1 not defined because of singularities)
            Estimate Std. Error z value Pr(>|z|)    
(Intercept)  3.00155    0.33709   8.904  < 2e-16 ***
EthN        -0.24591    0.39135  -0.628  0.52977    
SexM        -0.77181    0.38021  -2.030  0.04236 *  
AgeF1       -0.02546    0.41615  -0.061  0.95121    
AgeF2       -0.54884    0.54393  -1.009  0.31296    
AgeF3       -0.25735    0.40558  -0.635  0.52574    
LrnSL        0.38919    0.48421   0.804  0.42153    
EthN:SexM    0.36240    0.29430   1.231  0.21818    
EthN:AgeF1  -0.70000    0.43646  -1.604  0.10876    
EthN:AgeF2  -1.23283    0.42962  -2.870  0.00411 ** 
EthN:AgeF3   0.04721    0.44883   0.105  0.91622    
EthN:LrnSL   0.06847    0.34040   0.201  0.84059    
SexM:AgeF1   0.02257    0.47360   0.048  0.96198    
SexM:AgeF2   1.55330    0.51325   3.026  0.00247 ** 
SexM:AgeF3   1.25227    0.45539   2.750  0.00596 ** 
SexM:LrnSL   0.07187    0.40805   0.176  0.86019    
AgeF1:LrnSL -0.43101    0.47948  -0.899  0.36870    
AgeF2:LrnSL  0.52074    0.48567   1.072  0.28363    
AgeF3:LrnSL       NA         NA      NA       NA    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

(Dispersion parameter for Negative Binomial(1.6036) family taken to be 1)

    Null deviance: 235.23  on 145  degrees of freedom
Residual deviance: 167.53  on 128  degrees of freedom
AIC: 1100.5

Number of Fisher Scoring iterations: 1

              Theta:  1.604 
          Std. Err.:  0.214

 2 x log-likelihood:  -1062.546 
\end{Soutput}
\end{Schunk}

%% -- Summary/conclusions/discussion -------------------------------------------

\section{Summary and discussion} \label{sec:summary}

\begin{leftbar}
As usual \dots
\end{leftbar}

%% -- Optional special unnumbered sections -------------------------------------

\section*{Computational details}

\begin{leftbar}
If necessary or useful, information about certain computational details
such as version numbers, operating systems, or compilers could be included
in an unnumbered section. Also, auxiliary packages (say, for visualizations,
maps, tables, \dots) that are not cited in the main text can be credited here.
\end{leftbar}

The results in this paper were obtained using
\proglang{R}~3.5.1 with the
\pkg{MASS}~7.3.50 package. \proglang{R} itself
and all packages used are available from the Comprehensive
\proglang{R} Archive Network (CRAN) at
\url{https://CRAN.R-project.org/}.

\section*{Acknowledgments}

\begin{leftbar}
All acknowledgments (note the AE spelling) should be collected in this
unnumbered section before the references. It may contain the usual information
about funding and feedback from colleagues/reviewers/etc. Furthermore,
information such as relative contributions of the authors may be added here
(if any).
\end{leftbar}

%% -- Bibliography -------------------------------------------------------------
%% - References need to be provided in a .bib BibTeX database.
%% - All references should be made with \cite, \citet, \citep, \citealp etc.
%%   (and never hard-coded). See the FAQ for details.
%% - JSS-specific markup (\proglang, \pkg, \code) should be used in the .bib.
%% - Titles in the .bib should be in title case.
%% - DOIs should be included where available.

\bibliography{refs}

%% -- Appendix (if any) --------------------------------------------------------
%% - After the bibliography with page break.
%% - With proper section titles and _not_ just "Appendix".

\newpage

\begin{appendix}

\section{More technical details} \label{app:technical}

\begin{leftbar}
Appendices can be included after the bibliography (with a page break). Each
section within the appendix should have a proper section title (rather than
just \emph{Appendix}).

For more technical style details, please check out JSS's style FAQ at
\url{https://www.jstatsoft.org/pages/view/style#frequently-asked-questions}
which includes the following topics:
\begin{itemize}
  \item Title vs.\ sentence case.
  \item Graphics formatting.
  \item Naming conventions.
  \item Turning JSS manuscripts into \proglang{R} package vignettes.
  \item Trouble shooting.
  \item Many other potentially helpful details\dots
\end{itemize}
\end{leftbar}

\section[Using BibTeX]{Using \textsc{Bib}{\TeX}} \label{app:bibtex}

\begin{leftbar}
References need to be provided in a \textsc{Bib}{\TeX} file (\code{.bib}). All
references should be made with \verb|\cite|, \verb|\citet|, \verb|\citep|,
\verb|\citealp| etc.\ (and never hard-coded). This commands yield different
formats of author-year citations and allow to include additional details (e.g.,
pages, chapters, \dots) in brackets. In case you are not familiar with these
commands see the JSS style FAQ for details.

Cleaning up \textsc{Bib}{\TeX} files is a somewhat tedious task -- especially
when acquiring the entries automatically from mixed online sources. However,
it is important that informations are complete and presented in a consistent
style to avoid confusions. JSS requires the following format.
\begin{itemize}
  \item JSS-specific markup (\verb|\proglang|, \verb|\pkg|, \verb|\code|) should
    be used in the references.
  \item Titles should be in title case.
  \item Journal titles should not be abbreviated and in title case.
  \item DOIs should be included where available.
  \item Software should be properly cited as well. For \proglang{R} packages
    \code{citation("pkgname")} typically provides a good starting point.
\end{itemize}
\end{leftbar}

\end{appendix}

%% -----------------------------------------------------------------------------

\end{document}

### 2021-01-24 article/manuscript.Rnw
adding article

--- 2021-01-24 article/Untitled.Rnw
@@
 \author{Eric Weine\\University of Chicago
-   \And Mary Sara McPeek\\University of Chicago}
-\Plainauthor{Eric Weine, Mary Sara McPeek}
+   \And Mary Sara McPeek\\University of Chicago
+   \And Mark Abney\\University of Chicago}
+\Plainauthor{Eric Weine, Mary Sara McPeek, Mark Abney}
 
-\title{Efficient Calculation of Improved Simultaneous Testing Bands for QQplots}
+\title{Efficient Calculation of Improved Simultaneous Testing Bands for QQplots with \proglang{R} Package \pkg{qqconf}}
+\Plaintitle{Efficient Calculation of Improved Simultaneous Testing Bands for QQplots with R Package qqconf}
+\Shorttitle{Efficient Calculation of Simultaneous Testing Bands for QQplots with \pkg{qqconf}}
 %\author{Eric Weine and Mary Sara McPeek}
@@
 Current packages and algorithms towards this end either do not ensure a robust Type I error rate, are too slow, or are under-powered to deviations in the tails of the distribution.
-In this paper, we present an efficient algorithm that computes simultaneous testing bands for QQplots.
+In this paper, we present an efficient algorithm and accompanying \proglang{R} Package \pkg{qqconf} that computes simultaneous testing bands for QQplots.
 These bands have a variety of desirable properties, including being fast to compute and being equally sensitive to deviations in all parts of the null distribution, including the tails.
@@
 \Address{
+  Eric Weine\\
+  Department of Statistics\\
+  University of Chicago\\
+  924 E 57th St., Chicago, IL\\
+  E-mail: \email{ericweine15@gmail.com}\\
+  \\
   Mary Sara McPeek\\
@@
   E-mail: \email{mcpeek@uchicago.edu}\\
-  URL: \url{https://galton.uchicago.edu/~mcpeek/}
+  URL: \url{https://www.stat.uchicago.edu/~mcpeek/}\\
+  \\
+  Mark Abney\\
+  Department of Human Genetics\\
+  University of Chicago\\
+  920 E 58th St., Chicago, IL\\
+  E-mail: \email{abney@uchicago.edu}\\
+  URL: \url{https://hgen.uchicago.edu/program/faculty/mark-abney}
 }
+
 \begin{document}
@@
 A number of methods have been created towards this end.
-First, some available software puts pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic \citep{qqplotr}.
+First, some available software, like the \proglang{R} package \pkg{qqplotr}, puts pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic \citep{qqplotr}.
 This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified distribution.
-Second, the Komolgorov-Smirnov (KS) test is a common method for creating joint bands \citep{kolmogoroff1941confidence, smirnov1944approximate}.
+Second, the Komolgorov-Smirnov (KS) test, a part of the \pkg{stats} package in \proglang{R}, is a common method for creating joint bands \citep{kolmogoroff1941confidence, smirnov1944approximate}.
 While this method ensures the correct Type I error by using the distribution of the KS statistic, this test suffers from very low power under a variety of reasonable alternatives \citep{aldor2013power}.
@@
 This test has a variety of desirable properties, but because it requires simulation it is extremely slow in large datasets.
+It is also available in the package \pkg{qqplotr}.
 \newline
@@
 Suppose we have observations
-
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 and we are interested in conducting the following hypothesis test
-
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 with level $\alpha$, where all parameters of $F_{0}$ are known.
@@
 That is, we construct a set of intervals
-
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 and we reject $H_{0}$ if for any $i$
-
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 If we know the local level $\eta_{i}$, then
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $F_{i}$ is the CDF of the $i^{th}$ order statistic.
@@
 By this, we mean that we would like to design a test that applies equal scrutiny to each order statistic, and thus we set
-% an alternative explanation is that we're trying to design a test that would have optimum power under the alternative distribution where the probability of any of the order statistics being outside of the pointwise null region is equal.
+% 
 \begin{equation}
@@
 \end{equation}
-
+%
 This is known as ``equal local levels.''
@@
 \textbf{Step 1:} First, note that under the null hypothesis,
-
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 Thus, without loss of generality, we can build the algorithm for step 1 assuming that
-
+%
 \begin{equation*}
@@
 \end{equation*}
-% I'll worry about the uncertainty in parameter estimates later
-% I'll probably want some sort of a diagram here eventually
+% 
 We are trying to calculate the following probability
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 Where $P_{0}$ is the probability under the null hypothesis. It is easier to calculate this as
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 \newline
@@
 The key to the algorithm is that the following two events are the same:
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 where
-
+%
 \begin{align*}
@@
 \end{align*}
+%
 (See Figure 1 above for intuition).
@@
 Finally, we define
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 Our basic approach to step 1 is a recursive calculation of these $c_{w}^{(k)}$ values.
@@
 \end{algorithm}
+% Note, need to change all of the l values below to m's to match what the algorithm says above
+% Also need to finish writing out the algorithm
+% I can do all of this either tonight or tomorrow at some point
+% Then I also need to get the bibliography and to the pre-computation for the graphs.
 Now, we derive the algorithm. \textbf{Initialization:} (Lines 2 through 4 of Algorithm 1)
+%
 \begin{align*}
@@
 \end{align*}
+%
 Also, we initialize $l_{1} = 0$ and $u_{1} = 0$ because the only allowable partial sum is 0 in the first bin.
 \textbf{Recursion:} (Line 15 of Algorithm 1)
+%
 \begin{flalign*}
@@
 \end{flalign*}
+%
 \newline
@@
 First, we define the following values:
+%
 \begin{align*}
@@
 \end{align*}
+%
 Now, we make the following observations:
@@
 (6)
+%
 \begin{align*}
@@
 \end{align*}
+%
 This follows from (3) and (5). 
@@
 Combining the above results, we can write
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 Also, observe that for any $2 \leq r \leq 2n - 1$, we have
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 Thus, we can write 
+%
 \begin{align*}
@@
 \end{align*}
+%
 Now, if we let $r = n$ above, then we get 
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 which is line 21 in the psuedo-code above.
@@
 More precisely, it appears that the number of recursive steps required is very close to $8n^{2}$.
-While each recursive step itself requires calculating a binomial probability which is $O((n + 1)!)$ due to the calculation of the binomial coefficient multiplied by a quantity with powers as large as $n$, these calculations can be memoized with $O(n^{2})$ cost.
+While each recursive step itself requires calculating a binomial probability which is $O(n)$ due to the calculation of the binomial coefficient multiplied by a quantity with powers as large as $n$, these calculations can be memoized with $O(n^{2})$ cost.
 Thus, these binomial probability calculations do not change the big $O$ complexity of the algorithm.
@@
 Previously, Gontscharuk and Finner showed that the asymptotic local level for global level $\alpha$ and number of tests $n$ is
+%
 \begin{equation*}
@@
 \end{equation*}
+%
 \citep{gontscharuk2017asymptotics}.
@@
 To improve this approximation, they propose to add a smaller order correction term, resulting in an approximation of the form
+%
 \begin{equation}
@@
 \end{equation}
+%
 where $c_{\alpha}$ is chosen empirically.
@@
 \section{Examples}
-As noted above, the algorithm presented is only correct if all of the parameters of $F_{0}$ are known, and all $X_{1}, ..., X_{n}$ are independent.
-While both of these assumptions may only hold in a small number of cases, the methods above are still useful in a variety of scenarios.
+As noted above, the algorithm presented is suitable for the case when all of the parameters of $F_{0}$ are known, and all $X_{1}, ..., X_{n}$ are independent.
+While these assumptions may seem restrictive, the methods above are still useful in a variety of scenarios.
 \newline
 \newline
-One of the main advantages of the local levels method, is that it can easily be used to put testing bands onto QQplots by simply graphing each $(h_{i}, g_{i})$ interval.
+One of the main advantages of the local levels method compared to other global testing approaches, is that it can easily be used to put testing bands onto QQplots by simply graphing each $(h_{i}, g_{i})$ interval.
 This allows us to examine how a dataset might deviate from some null distribution much better than simply applying a test that yields a binary conclusion.
@@
 % This shouldn't be too difficult
-Suppose we have devised a new testing procedure to test a null hypothesis $H_{0}$ with test statistic $T(X_{1}, ..., X_{n})$, and we wish to establish that this test has correct Type I error rate.
+Suppose we have devised a new testing procedure to test a null hypothesis $H_{0}$ with test statistic $T$, where we also specify a particular method to calculate or approximate p-values.
+In such a situation it is important to perform some simulations under the null hypothesis and check that the resulting p-value distribution is approximately uniform in the simulation experiment.
 \newline
@@
 \newline
-(1) Generate $m$ simulated datasets: $(X_{1}^{(1)}, ..., X_{n}^{(1)}), ..., (X_{1}^{(m)}, ..., X_{n}^{(m)})$ under $H_{0}$.
+(1) Generate $n$ simulated datasets under $H_{0}$, and calculate $T$ for each siulated dataset to obtain $T_{1}, ..., T_{n}$.
 \newline
 \newline
-(2) Apply the test $T$ to each of these datasets at level $\alpha$ to yield $m$ reject / not-reject conclusions: $c_{1}, ..., c_{m}$, where $c_{i} = 1$ if $H_{0}$ is rejected and $0$ otherwise.
+(2) Select a value of $\alpha$, and for each of $T_{1}, ..., T_{n}$, determine whether the null hypothesis is rejected at level $\alpha$.
+Let $N_{\alpha}$ be the observed number of the $n$ tests that are rejected at level $\alpha$.
 \newline
 \newline
-(3) Conduct a test to confirm that the mean of $c_{1}, ..., c_{m}$ is $\alpha$.
+(3) Let $\alpha^{*}$ denote the true probability of rejection under the above procedure.
+Test the null hypothesis $H_{0}: \alpha^{*} = \alpha$ by applying, e.g., a z-test of proportions or an exact binomial test to the data $N_{\alpha}$.
 \newline
@@
 \newline
-(2) Apply the test $T$ to each of these datasets to yield $m$ p-values: $p_{1}, ..., p_{m}$.
+(2) For each $T_{i}$, calculate the corresponding p-value, $p_{i}$, to obtain $p_{1}, ..., p_{n}$.
 \newline
 \newline
-(3) Apply the local levels procedure to test if $p_{1}, ..., p_{m} \distras{iid} U(0, 1)$.
-% It seems to me that this would be an opportune time to make a comparison to the KS-test, but I'm not totally sure.
-% I should maybe put some graphs here as well.
+(3) Make a q-q plot comparing $p_{1}, ..., p_{n}$ to a $U(0, 1)$ distribution, and apply the local levels procedure to create simultaneous testing bands for the null hypothesis that $p_{1}, ..., p_{n} \distras{iid} U(0, 1)$.
 \newline
@@
 In Step 3, one could use many different testing bands.
-However, in the calibration of p-values, we typically don't have the expectation that our p-values would be more likely to deviate from uniform in some regions than others, and so it makes sense to use the local levels test because it is agnostic to the alternative distribution.
-Moreover, since it is generally most concerning if p-values are not calibrated in the lower tail of the distribution, the local levels test is preferable to the standard KS test because it is much more sensitive in the tails (Aldor-Noiman 2013).
+However, in the calibration of p-values, we typically don't have the expectation that our p-values would be more likely to deviate from uniform in any particular region, and so it makes sense to use the local levels test because it is agnostic to the alternative distribution.
+Moreover, since it is generally most concerning if small p-values are not calibrated, i.e.
+those in the lower tail of the uniform distribution, the local levels test is preferable to the standard KS test because it is much more sensitive in the tails (Aldor-Noiman 2013).
 
-\subsubsection{Chi-Square Test for Independence in a \texorpdfstring{$2 \times 2$}{2 X 2} Table}
+\subsubsection{Chi-Square Test for Independence in a $2$ X $2$ Table}
+We apply this approach to assess the calibration of p-values from the Pearson Chi-Square test for independence in a $2 \times 2$ table.
+A well-known rule of thumb is that the chi-square test is appropriate as long as the expected cell count in each cell under the null hypothesis is at least 5.
+We fix the cell probabilities under the null hypothesis and consider two different cases: in scenario 1, the sample size is $s=200$ and the rule of thumb holds, and scenario 2, the sample size is only $s=20$ and the rule of thumb does not hold.
+We use the local levels approach to generate simultaneous testing bands to assess the calibration of the p-values from the Pearson Chi-Square test for these two scenarios.\\
+
+More specifically, in each scenario, we randomly generate $n=1000$ $2 \times 2$ tables under the null hypothesis, where each table contains $s$ observations, with $s=200$ in scenario 1 and $s=20$ in scenario 2.
+For each table, the $s$ observations are i.i.d.\ with probability $q_{i,j}$ of falling in cell $(i,j)$, for $i=0,1, j=0,1$, where $q_{1,1} = a*b$, $q_{1,0} = a*(1-b)$, $q_{0,1} = (1-a)*b$, and $q_{0,0} = (1-a)*(1-b)$, with a=.15 and b=.4.
+For each table, let $X_{i,j}$ denote the observed count in cell $(i,j)$.
+If any table has $X_{0,0}+X_{0,1} = 0$ or $= s$, we discard the table and draw a new one, because that would imply that one of the rows of the table is empty, in which case the Pearson Chi-Squared test statistic is not defined.
+Similarly, if any table has $X_{0,0}+X_{1,0} = 0$ or $=s$, we discard the table and draw a new one.
+The code to do this is shown below:
+%
+<<contingency_tables>>=
+set.seed(8675309)
+# Generate contingency tables for variables as defined above
+generate_contingency_tables <- function(n, s, a, b) {
+
+  cell_probs <- c(a * b, a * (1 - b), b * (1 - a), (1 - b) * (1 - a))
+  num_sims <- 0
+  sim_mat <- matrix(NA, nrow = n, ncol = 4)
+
+  # Generate n simulations and append the contingency tables to a matrix
+  while (num_sims < n) {
+
+    proposed_sim <- t(rmultinom(n = 1, size = s, prob = cell_probs))
+
+    # Check to make sure that the chi-square statistic will be defined
+    if (proposed_sim[, 1] + proposed_sim[, 2] != 0 && 
+        proposed_sim[, 1] + proposed_sim[, 3] != 0 &&
+        proposed_sim[, 3] + proposed_sim[, 4] != 0 &&
+        proposed_sim[, 4] + proposed_sim[, 2]) {
+
+      num_sims <- num_sims + 1
+      sim_mat[num_sims, ] <- proposed_sim
+
+    }
+
+  }
+
+  return(sim_mat)
+
+}
+
+scenario_1 <- generate_contingency_tables(n = 1000, s = 200, a = .15, b = .4)
+scenario_2 <- generate_contingency_tables(n = 1000, s = 20, a = .15, b = .4)
+@
+%
+
+For each of the tables in the resulting sample, a Pearson chi-square test statistic is calculated as $T = \sum_{i=0}^1\sum_{j=0}^1 \frac{(X_{i,j}-q_{i,j})^2}{q_{i,j}}$, where $X_{i,j}$ is the observed count in cell $(i,j)$.
+For each scenario, this results in $n=1000$ test statistics, $T_1, \ldots, T_n$, one for each table.
+From these, we obtain $n=1000$ p-values, $p_1, \ldots, p_n$ by applying the $\chi^2_1$ approximation, i.e., $p_i = 1-F(T_i)$ for $i=1,\ldots, n$, where $F$ is taken to be the c.d.f.
+of the $\chi^2_1$ distribution.
+The code to do this is shown below:
+
+%
+<<p_values>>=
+# Compute Pearson Chi-Square Test p-values for Set of Contingency Tables
+get_p_values_from_c_tables <- function(c_tables, s) {
+
+  chisq_numerator <- (
+    (c_tables[, 1] * c_tables[, 4] - c_tables[, 2] * c_tables[, 3]) / s
+  ) ^ 2
+  chisq_denominator <- (c_tables[, 1] + c_tables[, 2]) * 
+    (c_tables[, 1] + c_tables[, 3]) * 
+    (c_tables[, 3] + c_tables[, 4]) * 
+    (c_tables[, 2] + c_tables[, 4]) / 
+    (s ^ 3)
+  chisq_stats_vec <- chisq_numerator / chisq_denominator
+  p_vals <- pchisq(q = chisq_stats_vec, df = 1, lower.tail = FALSE)
+  return(p_vals)
+
+}
+
+pvals_scenario_1 <- get_p_values_from_c_tables(scenario_1, s = 200)
+pvals_scenario_2 <- get_p_values_from_c_tables(scenario_2, s = 20)
+@
+%
+
+Figure 3 shows the resulting QQplots for scenarios 1 (in blue) and 2 (in red), where the 45$^{\mbox{\footnotesize o}}$ line is shown as well as the testing bands obtained from the equal local levels procedure for testing, at global level .05, the null hypothesis that $p_1, \ldots, p_n$ have the same distribution as $n$ i.i.d.\ draws from Unif(0,1).
+
+<<chisq_qq, fig=TRUE, include=FALSE>>=
+library(qqconf)
+bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
+
+# Plot 3: Q-Q plot of P-values from Chi-Squared Test
+# for Independence in a 2 x 2 Table
+
+plot(
+  bounds$x, 
+  sort(pvals_scenario_2), 
+  type = "l", 
+  col = "red", 
+  xlab = "Expected Uniform Quantile",
+  ylab = "Observed P-value"
+)
+
+# Add the 45-degree line to the plot
+lines(bounds$x, bounds$x)
+
+# Add the lower bound line for the level .05 
+# simultaneous testing bands from equal local levels.
+lines(bounds$x, bounds$lower_bound)
+
+# Add the upper bound line for the level .05 
+# simultaneous testing bands from equal local levels.
+lines(bounds$x, bounds$upper_bound)
+
+# Add the Q-Q plot for scenario 1.
+lines(bounds$x, sort(pvals_scenario_1), col = "blue")
+
+legend(
+  x = .02, 
+  y = .95, 
+  legend = c("s=20","s=200"), 
+  col = c("red","blue"), 
+  lty = 1
+)
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-chisq_qq}
+\end{center}
+\caption{QQplot for Scenario 1 and Scenario 2 With Standard Axes.}
+\end{figure}
+
+Figure 4 shows the same plots where the axes are transformed to be on the $-\log_{10}$ scale to focus the plot on small p-values.
+(Note that in Figure 4, small p-values are to the top and right of the plot, so a curve that is too low is conservative, and too high is anti-conservative.)
+
+<<chisq_qq_log, fig=TRUE, include=FALSE>>=
+# Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
+# from Chi-Squared Test for Independence in a 2 x 2 Table
+
+plot(
+  -log10(bounds$x), 
+  -log10(sort(pvals_scenario_2)),
+  type = "l",
+  col = "red",
+  xlab = "-log10(Expected Uniform Quantile)",
+  ylab = "-log10(Observed P-value)"
+)
+
+# Add the 45-degree line to the plot
+lines(-log10(bounds$x), -log10(bounds$x))
+
+# Add the lower bound line for the level .05 
+# simultaneous testing bands from equal local levels.
+lines(-log10(bounds$x), -log10(bounds$lower_bound))
+
+# Add the upper bound line for the level .05 
+# simultaneous testing bands from equal local levels.
+lines(-log10(bounds$x), -log10(bounds$upper_bound))
+
+# Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
+lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")
+
+legend(
+  x = .2, 
+  y = 3, 
+  legend = c("s=20", "s=200"), 
+  col = c("red","blue"), 
+  lty = 1
+)
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-chisq_qq_log}
+\end{center}
+\caption{QQplot for Scenario 1 and Scenario 2 With Axes On Log Scale.}
+\end{figure}
+
+From these plots, it can be seen that in scenario 1, when $s=200$ and the smallest expected cell count is 12, there is no significant deviation of the p-values from i.i.d.\ Unif(0,1) under the null hypothesis.
+In contrast, in scenario 2, when $s=20$ and the smallest expected cell count is 1.2, the $\chi^2_1$ asymptotic distribution is not an accurate approximation to the sampling distribution of $T$.
+As a result, we can see in Figures 3 and 4 that the p-values differ significantly from i.i.d.\ Unif(0,1) under the null hypothesis, with small p-values tending to be overly conservative, while the larger p-values tend to be anti-conservative.
+
+\subsection{Multiple Testing in Genome Wide Association Studies}
+In genome wide association studies (GWAS), we are interested in identifying the genetic variants that are responsible for biological traits.
+Often, we test a large number of single-nucleotide polymorphisms (SNPs), to see if any of them are strongly correlated with some discrete or continuous trait.
+Often, it is useful to test the following global null hypothesis:
+\newline
+\newline
+$H_{0}$: All genome-wide SNPs in some functional category have correlation 0 with the trait of interest.
+%
+\begin{equation*}
+\textrm{ vs. }
+\end{equation*}
+%
+\noindent$H_{A}$: At least one SNP in some functional category has non-zero correlation with the trait of interest.
+\newline
+\newline
+Typically, when testing this global null, we apply some test to each of $n$ SNPs, yielding $n$ p-values.
+While the SNPs have a local correlation structure, this has only a weak effect at a genome-wide scale.
+Thus, the local levels procedure still provides a valuable visualization tool to assess the extent and type of any deviation from the null, even though it is not exact.
+Particularly in genetics, if the p-values deviate from the null, it can be very useful to view graphically how they deviate.
+For instance, if there are a few very large p-values but the rest of the distribution looks relatively uniform, then this indicates that the trait of interest is driven by a few mutations.
+If, however, there are some small deviations throughout the p-value distribution, then this indicates that trait of interest is driven by a number of genes that all play some small part in a complex biological process, or potentially by some confounding variables that are not controlled for.
+\newline
+\newline
+If a very specific distribution for $H_{A}$ is suspected, then it makes sense to use a test that has high power under this alternative, which may not be our local levels test.
+However, in the general case when little is known about the alternative distribution, using local levels is desirable because it is agnostic to alternative distributions.
+Moreover, since small p-values are often of great interest in GWAS because they can indicate the main biological drivers of a trait, the local levels test is far superior to the KS test due to its tail sensitivity.
+%Here is where the biological example goes with the code. I want to have the graphs that I make from this and then I also want
+\section{Discussion}
+The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for QQplots.
+Of course, our method is limited by the assumptions that (1) all of the tests are independent and that (2) all of the parameters of the null distribution are known.
+Currently, we are not aware of methods to handle the dependent case that allow for bands on QQplots.
+To handle the second issue, Aldor-Noiman has adapted their method such that it will yield exact results when some parameters of the null distribution are unknown.
+However, if the dataset is very large, Aldor-Noiman's method is prohibitively slow.
+In this case, we suggest that our method be used because it is much faster, and with a sufficiently large dataset the uncertainty in the parameters will become negligible under standard regularity conditions.
+Methods to handle parameter uncertainty with an exact calculation have been discussed in the context of the normal distribution \citep{rosenkrantz2000confidence}, but a general method towards this end has not been developed, and would be an important next step.
+\newline
+\newline
+Our software is available on CRAN.
+To aid in computation speed, we have pre-computed a number of different local level values given a global level and the size of the dataset.
+This computes the testing bands very quickly with little error.
+We have also implemented a one-sided test for the case in which we are only concerned with values that are smaller than would be expected under the null (e.g.
+we only care about small p-values).
 
 \bibliography{refs}
+%\bibliographystyle{ieeetr}
+
 \end{document}

### 2021-01-24 article/manuscript.tex
adding article

--- 2021-01-24 article/manuscript.Rnw
@@
 %% need no \usepackage{Sweave}
-\SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
-<<preliminaries, echo=FALSE, results=hide>>=
-options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
-library("MASS")
-@
+
 \raggedbottom
@@
 %
-<<contingency_tables>>=
-set.seed(8675309)
-# Generate contingency tables for variables as defined above
-generate_contingency_tables <- function(n, s, a, b) {
-
-  cell_probs <- c(a * b, a * (1 - b), b * (1 - a), (1 - b) * (1 - a))
-  num_sims <- 0
-  sim_mat <- matrix(NA, nrow = n, ncol = 4)
-
-  # Generate n simulations and append the contingency tables to a matrix
-  while (num_sims < n) {
-
-    proposed_sim <- t(rmultinom(n = 1, size = s, prob = cell_probs))
-
-    # Check to make sure that the chi-square statistic will be defined
-    if (proposed_sim[, 1] + proposed_sim[, 2] != 0 && 
-        proposed_sim[, 1] + proposed_sim[, 3] != 0 &&
-        proposed_sim[, 3] + proposed_sim[, 4] != 0 &&
-        proposed_sim[, 4] + proposed_sim[, 2]) {
-
-      num_sims <- num_sims + 1
-      sim_mat[num_sims, ] <- proposed_sim
-
-    }
-
-  }
-
-  return(sim_mat)
-
-}
-
-scenario_1 <- generate_contingency_tables(n = 1000, s = 200, a = .15, b = .4)
-scenario_2 <- generate_contingency_tables(n = 1000, s = 20, a = .15, b = .4)
-@
+\begin{Schunk}
+\begin{Sinput}
+R> set.seed(8675309)
+R> # Generate contingency tables for variables as defined above
+R> generate_contingency_tables <- function(n, s, a, b) {
++    
++    cell_probs <- c(a * b, a * (1 - b), b * (1 - a), (1 - b) * (1 - a))
++    num_sims <- 0
++    sim_mat <- matrix(NA, nrow = n, ncol = 4)
++    
++    # Generate n simulations and append the contingency tables to a matrix
++    while (num_sims < n) {
++      
++      proposed_sim <- t(rmultinom(n = 1, size = s, prob = cell_probs))
++      
++      # Check to make sure that the chi-square statistic will be defined
++      if (proposed_sim[, 1] + proposed_sim[, 2] != 0 && 
++          proposed_sim[, 1] + proposed_sim[, 3] != 0 &&
++          proposed_sim[, 3] + proposed_sim[, 4] != 0 &&
++          proposed_sim[, 4] + proposed_sim[, 2]) {
++        
++        num_sims <- num_sims + 1
++        sim_mat[num_sims, ] <- proposed_sim
++        
++      }
++      
++    }
++    
++    return(sim_mat)
++    
++  }
+R> scenario_1 <- generate_contingency_tables(n = 1000, s = 200, a = .15, b = .4)
+R> scenario_2 <- generate_contingency_tables(n = 1000, s = 20, a = .15, b = .4)
+\end{Sinput}
+\end{Schunk}
 %
@@
 %
-<<p_values>>=
-# Compute Pearson Chi-Square Test p-values for Set of Contingency Tables
-get_p_values_from_c_tables <- function(c_tables, s) {
-
-  chisq_numerator <- (
-    (c_tables[, 1] * c_tables[, 4] - c_tables[, 2] * c_tables[, 3]) / s
-  ) ^ 2
-  chisq_denominator <- (c_tables[, 1] + c_tables[, 2]) * 
-    (c_tables[, 1] + c_tables[, 3]) * 
-    (c_tables[, 3] + c_tables[, 4]) * 
-    (c_tables[, 2] + c_tables[, 4]) / 
-    (s ^ 3)
-  chisq_stats_vec <- chisq_numerator / chisq_denominator
-  p_vals <- pchisq(q = chisq_stats_vec, df = 1, lower.tail = FALSE)
-  return(p_vals)
-
-}
-
-pvals_scenario_1 <- get_p_values_from_c_tables(scenario_1, s = 200)
-pvals_scenario_2 <- get_p_values_from_c_tables(scenario_2, s = 20)
-@
+\begin{Schunk}
+\begin{Sinput}
+R> # Compute Pearson Chi-Square Test p-values for Set of Contingency Tables
+R> get_p_values_from_c_tables <- function(c_tables, s) {
++    
++    chisq_numerator <- (
++      (c_tables[, 1] * c_tables[, 4] - c_tables[, 2] * c_tables[, 3]) / s
++    ) ^ 2
++    chisq_denominator <- (c_tables[, 1] + c_tables[, 2]) * 
++      (c_tables[, 1] + c_tables[, 3]) * 
++      (c_tables[, 3] + c_tables[, 4]) * 
++      (c_tables[, 2] + c_tables[, 4]) / 
++      (s ^ 3)
++    chisq_stats_vec <- chisq_numerator / chisq_denominator
++    p_vals <- pchisq(q = chisq_stats_vec, df = 1, lower.tail = FALSE)
++    return(p_vals)
++    
++  }
+R> pvals_scenario_1 <- get_p_values_from_c_tables(scenario_1, s = 200)
+R> pvals_scenario_2 <- get_p_values_from_c_tables(scenario_2, s = 20)
+\end{Sinput}
+\end{Schunk}
 %
@@
 
-<<chisq_qq, fig=TRUE, include=FALSE>>=
-library(qqconf)
-bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
-
-# Plot 3: Q-Q plot of P-values from Chi-Squared Test
-# for Independence in a 2 x 2 Table
-
-plot(
-  bounds$x, 
-  sort(pvals_scenario_2), 
-  type = "l", 
-  col = "red", 
-  xlab = "Expected Uniform Quantile",
-  ylab = "Observed P-value"
-)
-
-# Add the 45-degree line to the plot
-lines(bounds$x, bounds$x)
-
-# Add the lower bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(bounds$x, bounds$lower_bound)
-
-# Add the upper bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(bounds$x, bounds$upper_bound)
-
-# Add the Q-Q plot for scenario 1.
-lines(bounds$x, sort(pvals_scenario_1), col = "blue")
-
-legend(
-  x = .02, 
-  y = .95, 
-  legend = c("s=20","s=200"), 
-  col = c("red","blue"), 
-  lty = 1
-)
-@
+\begin{Schunk}
+\begin{Sinput}
+R> library(qqconf)
+R> bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
+R> # Plot 3: Q-Q plot of P-values from Chi-Squared Test
+R> # for Independence in a 2 x 2 Table
+R> 
+R> plot(
++    bounds$x, 
++    sort(pvals_scenario_2), 
++    type = "l", 
++    col = "red", 
++    xlab = "Expected Uniform Quantile",
++    ylab = "Observed P-value"
++  )
+R> # Add the 45-degree line to the plot
+R> lines(bounds$x, bounds$x)
+R> # Add the lower bound line for the level .05 
+R> # simultaneous testing bands from equal local levels.
+R> lines(bounds$x, bounds$lower_bound)
+R> # Add the upper bound line for the level .05 
+R> # simultaneous testing bands from equal local levels.
+R> lines(bounds$x, bounds$upper_bound)
+R> # Add the Q-Q plot for scenario 1.
+R> lines(bounds$x, sort(pvals_scenario_1), col = "blue")
+R> legend(
++    x = .02, 
++    y = .95, 
++    legend = c("s=20","s=200"), 
++    col = c("red","blue"), 
++    lty = 1
++  )
+\end{Sinput}
+\end{Schunk}
 
@@
 
-<<chisq_qq_log, fig=TRUE, include=FALSE>>=
-# Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
-# from Chi-Squared Test for Independence in a 2 x 2 Table
-
-plot(
-  -log10(bounds$x), 
-  -log10(sort(pvals_scenario_2)),
-  type = "l",
-  col = "red",
-  xlab = "-log10(Expected Uniform Quantile)",
-  ylab = "-log10(Observed P-value)"
-)
-
-# Add the 45-degree line to the plot
-lines(-log10(bounds$x), -log10(bounds$x))
-
-# Add the lower bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(-log10(bounds$x), -log10(bounds$lower_bound))
-
-# Add the upper bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(-log10(bounds$x), -log10(bounds$upper_bound))
-
-# Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
-lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")
-
-legend(
-  x = .2, 
-  y = 3, 
-  legend = c("s=20", "s=200"), 
-  col = c("red","blue"), 
-  lty = 1
-)
-@
+\begin{Schunk}
+\begin{Sinput}
+R> # Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
+R> # from Chi-Squared Test for Independence in a 2 x 2 Table
+R> 
+R> plot(
++    -log10(bounds$x), 
++    -log10(sort(pvals_scenario_2)),
++    type = "l",
++    col = "red",
++    xlab = "-log10(Expected Uniform Quantile)",
++    ylab = "-log10(Observed P-value)"
++  )
+R> # Add the 45-degree line to the plot
+R> lines(-log10(bounds$x), -log10(bounds$x))
+R> # Add the lower bound line for the level .05 
+R> # simultaneous testing bands from equal local levels.
+R> lines(-log10(bounds$x), -log10(bounds$lower_bound))
+R> # Add the upper bound line for the level .05 
+R> # simultaneous testing bands from equal local levels.
+R> lines(-log10(bounds$x), -log10(bounds$upper_bound))
+R> # Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
+R> lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")
+R> legend(
++    x = .2, 
++    y = 3, 
++    legend = c("s=20", "s=200"), 
++    col = c("red","blue"), 
++    lty = 1
++  )
+\end{Sinput}
+\end{Schunk}
 

### 2021-04-24 article/manuscript.Rnw
article updated

@@
 \usepackage{eqparbox}
+\usepackage{hyperref}
 %% new custom commands
@@
 Quantile-Quantile plots (QQplots) are a common statistical tool used to judge if a sample comes from a specified distribution \citep{wilk_gnanadesikan_1968}.
-Despite their ubiquity, they are often difficult to interpret because it is challenging to determine if the magnitude of the deviation from the specified distribution is large enough to indicate a lack of fit as opposed to sampling variance.
+Despite their ubiquity, they are often difficult to interpret because it is challenging to determine if the magnitude of the deviation from the specified distribution is large enough to indicate a lack of fit as opposed to sampling variability.
 To make this determination, it is useful to put testing bands on a QQplot.
@@
 A number of methods have been created towards this end.
-First, some available software, like the \proglang{R} package \pkg{qqplotr}, puts pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic \citep{qqplotr}.
-This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified distribution.
-Second, the Komolgorov-Smirnov (KS) test, a part of the \pkg{stats} package in \proglang{R}, is a common method for creating joint bands \citep{kolmogoroff1941confidence, smirnov1944approximate}.
-While this method ensures the correct Type I error by using the distribution of the KS statistic, this test suffers from very low power under a variety of reasonable alternatives \citep{aldor2013power}.
-In the same work, Aldor-Noiman et al.
-introduced a much more powerful test (under most alternatives) called the Tail Sensitive (TS) test.
-This test uses simulation to conduct an $\eta$ level test on each order statistic such that the overall test has an $\alpha$ level Type I error.
-This test has a variety of desirable properties, but because it requires simulation it is extremely slow in large datasets.
-It is also available in the package \pkg{qqplotr}.
+Naively, one could put pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic of the sample.
+This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution.
+To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}.
+While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power}.
+A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2016goodness}.
+Because this test, which will be referred to as equal local levels (ELL), conducts an $\eta$ level test on each order statistic, it is agnostic to any alternative distribution.
+This makes ELL a sensible choice for a standard test to use in creating testing bands on QQplots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
 \newline
 \newline
-In what follows, we present a method that yields the same results as the TS test but does so substantially faster because of an efficient recursive calculation.
-We then demonstrate this test on a few multiple testing scenarios including Type I error calibration and genetic studies.
+Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for QQplots on real data.
+While the base-\proglang{R} package \pkg{stats} provides functionality for creating a QQplot to compare a sample against the normal distribution, it doesn't give the user the ability to create QQplots for other distributions or to put testing bands on those plots.
+The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create QQplots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
+However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes.
+\newline
+\newline
+In what follows, we introduce the \proglang{R} package \pkg{qqconf}.
+With the aid of a novel recursive calculation developed below, \pkg{qqconf} can quickly provide ELL testing bands for comparing even very large samples to any reference distribution with a CDF implemented.
+In addition to these testing bands, \pkg{qqconf} provides a variety of plotting functionalities that allow the user to easily visualize where any deviation of the sample from the null distribution may occur.
+In section \hyperref[sec:methods]{2}, we introduce the methods required for the efficient recursive calculation mentioned above.
+In section \hyperref[sec:methods]{3}, we discuss the behavior of ELL bands in large sample sizes and an approximation to these bands that makes them very easy to calculate for even very large samples ($n > 5 \cdot 10^{6}$).
+In section \hyperref[sec:examples]{4}, we introduce \pkg{qqconf} and demonstrate its functionality on a few multiple testing scenarios including including Type I error calibration and genetic studies.
+Finally, we conclude in section \hyperref[sec:discussion]{5} with a discussion of limitations the of ELL and \pkg{qqconf} as well as further directions for creating testing bands on QQplots.
 \section{Methods}
+\label{sec:methods}
 
@@
 \section{Local Level Approximations in Large Samples}
+\label{sec:approx}
 For sufficiently large values of the number of tests $n$, it can be expedient to apply an accurate asymptotic approximation of the local level $\eta$ corresponding to global level $\alpha$ in place of exact computation.
@@
 \section{Examples}
+\label{sec:examples}
 As noted above, the algorithm presented is suitable for the case when all of the parameters of $F_{0}$ are known, and all $X_{1}, ..., X_{n}$ are independent.
@@
 library(qqconf)
+n <- 1000
 bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
@@
 plot(
-  bounds$x, 
+  c(1:n) / (n + 1), 
   sort(pvals_scenario_2), 
@@
 
-# Add the 45-degree line to the plot
-lines(bounds$x, bounds$x)
+# Add the Q-Q plot for scenario 1.
+lines(c(1:n) / (n + 1), sort(pvals_scenario_1), col = "blue")
 
-# Add the lower bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(bounds$x, bounds$lower_bound)
-
-# Add the upper bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(bounds$x, bounds$upper_bound)
-
-# Add the Q-Q plot for scenario 1.
-lines(bounds$x, sort(pvals_scenario_1), col = "blue")
+qq_conf_plot(
+  obs = pvals_scenario_2,
+  distribution = qunif,
+  method = "ell",
+  alpha = .05, 
+  add = TRUE
+)
 
@@
 \section{Discussion}
+\label{sec:methods}
 The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for QQplots.

### 2021-04-24 article/manuscript.tex
article updated

@@
 R> library(qqconf)
+R> n <- 1000
 R> bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
@@
 R> plot(
-+    bounds$x, 
++    c(1:n) / (n + 1), 
 +    sort(pvals_scenario_2), 
@@
 +  )
-R> # Add the 45-degree line to the plot
-R> lines(bounds$x, bounds$x)
-R> # Add the lower bound line for the level .05 
-R> # simultaneous testing bands from equal local levels.
-R> lines(bounds$x, bounds$lower_bound)
-R> # Add the upper bound line for the level .05 
-R> # simultaneous testing bands from equal local levels.
-R> lines(bounds$x, bounds$upper_bound)
 R> # Add the Q-Q plot for scenario 1.
-R> lines(bounds$x, sort(pvals_scenario_1), col = "blue")
+R> lines(c(1:n) / (n + 1), sort(pvals_scenario_1), col = "blue")
+R> qq_conf_plot(
++    obs = pvals_scenario_2,
++    distribution = qunif,
++    method = "ell",
++    alpha = .05, 
++    add = TRUE
++  )
 R> legend(

### 2021-04-24 qqconf/R/qqplot.R
added additional parameter

@@ -35,6 +35,8 @@
 #'   (i.e. tol, max_it, method).
 #' @param pw.lty Line type for the pointwise error bounds. Set to non-zero for a line.
 #' @param pw.col Color for the pointwise bounds line.
+#' @param samples_func Function used to plot sample points on the graph.
+#' @param sample_col Color of the samples
 #' @param ... Additional parameters for the plot.
 #' 
 #' @export
@@ -57,6 +59,8 @@ qq_conf_plot <- function(obs,
                          bounds_params = NULL,
                          pw.lty = 0,
                          pw.col = 'black',
+                         samples_func = points,
+                         samples_col = 'black',
                          ...) {
   
   dist_name <- as.character(substitute(distribution))
@@ -228,7 +232,7 @@ qq_conf_plot <- function(obs,
       lines(exp.pts, pointwise.high, lty = pw.lty, col = pw.col, ...)
     }
   }
-  points(exp.pts[2:(samp.size + 1)], y.pts, ...)
+  do.call(samples_func, c(list(x = exp.pts[2:(samp.size + 1)], y = y.pts, col = samples_col), ...))
   if (difference) {
     abline(h = 0, ...)
   } else {

### 2021-04-25 article/manuscript.Rnw
changed article to include examples with our code

@@
 
-plot(
-  c(1:n) / (n + 1), 
-  sort(pvals_scenario_2), 
-  type = "l", 
-  col = "red", 
-  xlab = "Expected Uniform Quantile",
-  ylab = "Observed P-value"
+qq_conf_plot(
+  obs = pvals_scenario_2,
+  distribution = qunif,
+  method = "ell",
+  alpha = .05,
+  samples_func = lines,
+  samples_col = "red"
 )
@@
 
-qq_conf_plot(
-  obs = pvals_scenario_2,
-  distribution = qunif,
-  method = "ell",
-  alpha = .05, 
-  add = TRUE
-)
-
 legend(
-  x = .02, 
-  y = .95, 
+  "topleft", 
   legend = c("s=20","s=200"), 
@@
 # from Chi-Squared Test for Independence in a 2 x 2 Table
+n <- 1000
 
-plot(
-  -log10(bounds$x), 
-  -log10(sort(pvals_scenario_2)),
-  type = "l",
-  col = "red",
-  xlab = "-log10(Expected Uniform Quantile)",
-  ylab = "-log10(Observed P-value)"
+qq_conf_plot(
+  obs = pvals_scenario_2,
+  distribution = qunif,
+  method = "ell",
+  alpha = .05,
+  samples_func = lines,
+  samples_col = "red",
+  log10 = TRUE
 )
 
-# Add the 45-degree line to the plot
-lines(-log10(bounds$x), -log10(bounds$x))
-
-# Add the lower bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(-log10(bounds$x), -log10(bounds$lower_bound))
-
-# Add the upper bound line for the level .05 
-# simultaneous testing bands from equal local levels.
-lines(-log10(bounds$x), -log10(bounds$upper_bound))
-
-# Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
-lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")
+# Add the Q-Q plot for scenario 1.
+lines(-log10(c(1:n) / (n + 1)), -log10(sort(pvals_scenario_1)), col = "blue")
 
 legend(
-  x = .2, 
-  y = 3, 
-  legend = c("s=20", "s=200"), 
+  "topleft",
+  legend = c("s=20","s=200"), 
   col = c("red","blue"), 

### 2021-04-25 article/manuscript.tex
changed article to include examples with our code

@@
 R> 
-R> plot(
-+    c(1:n) / (n + 1), 
-+    sort(pvals_scenario_2), 
-+    type = "l", 
-+    col = "red", 
-+    xlab = "Expected Uniform Quantile",
-+    ylab = "Observed P-value"
-+  )
-R> # Add the Q-Q plot for scenario 1.
-R> lines(c(1:n) / (n + 1), sort(pvals_scenario_1), col = "blue")
+R> 
 R> qq_conf_plot(
@@
 +    alpha = .05,
-+    add = TRUE
++    samples_func = lines,
++    samples_col = "red"
 +  )
+R> # Add the Q-Q plot for scenario 1.
+R> lines(c(1:n) / (n + 1), sort(pvals_scenario_1), col = "blue")
 R> legend(
-+    x = .02, 
-+    y = .95, 
++    "topleft", 
 +    legend = c("s=20","s=200"), 
@@
 R> # from Chi-Squared Test for Independence in a 2 x 2 Table
-R> 
-R> plot(
-+    -log10(bounds$x), 
-+    -log10(sort(pvals_scenario_2)),
-+    type = "l",
-+    col = "red",
-+    xlab = "-log10(Expected Uniform Quantile)",
-+    ylab = "-log10(Observed P-value)"
+R> n <- 1000
+R> qq_conf_plot(
++    obs = pvals_scenario_2,
++    distribution = qunif,
++    method = "ell",
++    alpha = .05,
++    samples_func = lines,
++    samples_col = "red",
++    log10 = TRUE
 +  )
-R> # Add the 45-degree line to the plot
-R> lines(-log10(bounds$x), -log10(bounds$x))
-R> # Add the lower bound line for the level .05 
-R> # simultaneous testing bands from equal local levels.
-R> lines(-log10(bounds$x), -log10(bounds$lower_bound))
-R> # Add the upper bound line for the level .05 
-R> # simultaneous testing bands from equal local levels.
-R> lines(-log10(bounds$x), -log10(bounds$upper_bound))
-R> # Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
-R> lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")
+R> # Add the Q-Q plot for scenario 1.
+R> lines(-log10(c(1:n) / (n + 1)), -log10(sort(pvals_scenario_1)), col = "blue")
 R> legend(
-+    x = .2, 
-+    y = 3, 
-+    legend = c("s=20", "s=200"), 
++    "topleft",
++    legend = c("s=20","s=200"), 
 +    col = c("red","blue"), 

### 2021-04-25 qqconf/R/qqplot.R

@@ -151,16 +151,26 @@ qq_conf_plot <- function(obs,
   conf <- c(alpha / 2, conf.int + alpha / 2)
   ## The observed and expected quantiles. Expected quantiles are based on the specified
   ## distribution
+  # constant for visual expansion of confidence regions
+  c <- .5
   obs.pts <- sort(obs)
   exp.pts <- do.call(distribution, c(list(p=ppoints(samp.size, a=0)), dparams))
   if (log10 == TRUE) {
     exp.pts <- -log10(exp.pts)
+    low_exp_pt <- c * -log10(do.call(distribution, c(list(p=c(1 / (samp.size * 1.25)))))) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * -log10(do.call(distribution, c(list(p=1 - c(1 / (samp.size * 1.25)))))) + (1 - c) * exp.pts[samp.size]
     if (any(obs.pts <= 0)) {
       
       stop("log10 scaling can only be used with strictly positive distributions.")
       
     }
     obs.pts <- -log10(obs.pts)
+  }
+  else {
+    
+    low_exp_pt <- c * do.call(distribution, c(list(p=c(1 / (samp.size * 1.25))))) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * do.call(distribution, c(list(p=1 - c(1 / (samp.size * 1.25))))) + (1 - c) * exp.pts[samp.size]
+    
   }
   if (difference) {
     y.pts <- obs.pts - exp.pts
@@ -199,16 +209,6 @@ qq_conf_plot <- function(obs,
       global.high <- do.call(distribution, c(list(p = up), dparams))
       
     }
-
-    # code to extend region for visibility
-    global.low <- c(global.low[1], global.low, global.low[samp.size])
-    global.high <- c(global.high[1], global.high, global.high[samp.size])
-    pointwise.low <- c(pointwise.low[1], pointwise.low, pointwise.low[samp.size])
-    pointwise.high <- c(pointwise.high[1], pointwise.high, pointwise.high[samp.size])
-    c <- .5
-    low_exp_pt <- c * do.call(distribution, c(list(p=c(1 / (samp.size * 1.25))))) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * do.call(distribution, c(list(p=1 - c(1 / (samp.size * 1.25))))) + (1 - c) * exp.pts[samp.size]
-    exp.pts <- c(low_exp_pt, exp.pts, high_exp_pt)
     
[…]

### 2021-04-25 article/manuscript.Rnw
added code to set min and max on ci addition

@@
 While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power}.
-A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2016goodness}.
+A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness}.
 Because this test, which will be referred to as equal local levels (ELL), conducts an $\eta$ level test on each order statistic, it is agnostic to any alternative distribution.

### 2021-04-25 qqconf/R/qqplot.R

@@ -152,13 +152,13 @@ qq_conf_plot <- function(obs,
   ## The observed and expected quantiles. Expected quantiles are based on the specified
   ## distribution
   # constant for visual expansion of confidence regions
-  c <- .5
+  c <- .5 
   obs.pts <- sort(obs)
   exp.pts <- do.call(distribution, c(list(p=ppoints(samp.size, a=0)), dparams))
   if (log10 == TRUE) {
     exp.pts <- -log10(exp.pts)
-    low_exp_pt <- c * -log10(do.call(distribution, c(list(p=c(1 / (samp.size * 1.25)))))) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * -log10(do.call(distribution, c(list(p=1 - c(1 / (samp.size * 1.25)))))) + (1 - c) * exp.pts[samp.size]
+    low_exp_pt <- c * -log10(do.call(distribution, c(list(p=c(1 / max(samp.size * 1.25, samp.size + 2)))))) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * -log10(do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2)))))) + (1 - c) * exp.pts[samp.size]
     if (any(obs.pts <= 0)) {
       
       stop("log10 scaling can only be used with strictly positive distributions.")
@@ -168,8 +168,8 @@ qq_conf_plot <- function(obs,
   }
   else {
     
-    low_exp_pt <- c * do.call(distribution, c(list(p=c(1 / (samp.size * 1.25))))) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * do.call(distribution, c(list(p=1 - c(1 / (samp.size * 1.25))))) + (1 - c) * exp.pts[samp.size]
+    low_exp_pt <- c * do.call(distribution, c(list(p=c(1 / max(samp.size * 1.25, samp.size + 2))))) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2))))) + (1 - c) * exp.pts[samp.size]
     
   }
   if (difference) {
@@ -241,7 +241,6 @@ qq_conf_plot <- function(obs,
     }
   }
   do.call(samples_func, c(list(x = exp.pts[2:(samp.size + 1)], y = y.pts, col = samples_col), ...))
[…]

### 2021-04-26 article/manuscript.Rnw
pushed article updates

--- 2021-04-25 article/manuscript.Rnw
@@
 
-\title{Efficient Calculation of Improved Simultaneous Testing Bands for QQplots with \proglang{R} Package \pkg{qqconf}}
-\Plaintitle{Efficient Calculation of Improved Simultaneous Testing Bands for QQplots with R Package qqconf}
-\Shorttitle{Efficient Calculation of Simultaneous Testing Bands for QQplots with \pkg{qqconf}}
-%\author{Eric Weine and Mary Sara McPeek}
+\title{Application of Equal Local Levels to Improve Q-Q Plot Testing Bands with \proglang{R} Package \pkg{qqconf}}
+\Plaintitle{Application of Equal Local Levels to Improve Q-Q Plot Testing Bands with R Package qqconf}
+\Shorttitle{Equal Local Levels Q-Q Plot Testing Bands with \pkg{qqconf}}
 \Abstract{
-  Quantile-Quantile plots (QQplots) are often difficult to interpret because it is unclear how large the deviation from the theoretical distribution must be to indicate a lack of fit.
+  Quantile-Quantile plots (Q-Q plots) are often difficult to interpret because it is unclear how large the deviation from the theoretical distribution must be to indicate a lack of fit.
 Current packages and algorithms towards this end either do not ensure a robust Type I error rate, are too slow, or are under-powered to deviations in the tails of the distribution.
-In this paper, we present an efficient algorithm and accompanying \proglang{R} Package \pkg{qqconf} that computes simultaneous testing bands for QQplots.
+In this paper, we present an efficient algorithm and accompanying \proglang{R} Package \pkg{qqconf} that computes simultaneous testing bands for Q-Q plots.
 These bands have a variety of desirable properties, including being fast to compute and being equally sensitive to deviations in all parts of the null distribution, including the tails.
@@
 
-\Keywords{QQplots, Equal Local Levels, Kolmolgorov-Smirnov, GWAS, Multiple Testing}
+\Keywords{Q-Q plots, Equal Local Levels, Kolmolgorov-Smirnov, GWAS, Multiple Testing}
 
@@
 \section{Introduction}
-Quantile-Quantile plots (QQplots) are a common statistical tool used to judge if a sample comes from a specified distribution \citep{wilk_gnanadesikan_1968}.
+Quantile-Quantile plots (Q-Q plots) are a common statistical tool used to judge if a sample comes from a specified distribution \citep{wilk_gnanadesikan_1968}.
 Despite their ubiquity, they are often difficult to interpret because it is challenging to determine if the magnitude of the deviation from the specified distribution is large enough to indicate a lack of fit as opposed to sampling variability.
-To make this determination, it is useful to put testing bands on a QQplot.
+To make this determination, it is useful to put testing bands on a Q-Q plot.
 \newline
@@
 A number of methods have been created towards this end.
-Naively, one could put pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic of the sample.
+Naively, one could put pointwise testing bands onto Q-Q plots, which conduct $\alpha$ level tests on each order statistic of the sample.
 This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution.
 To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}.
-While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power}.
-A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2016goodness}.
-Because this test, which will be referred to as equal local levels (ELL), conducts an $\eta$ level test on each order statistic, it is agnostic to any alternative distribution.
-This makes ELL a sensible choice for a standard test to use in creating testing bands on QQplots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
+While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power, berk1979goodness}.
+A more promising approach would be to apply the equal local levels method (ELL) to create testing bands.
+This method, originally introduced by Berk and Jones and later developed by Gontscharuk et al.
+as an alternative testing procedure to higher-criticism and KS, conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness, gontscharuk2017asymptotics}.
+Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution.
+While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test in this use case, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
 \newline
 \newline
-Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for QQplots on real data.
-While the base-\proglang{R} package \pkg{stats} provides functionality for creating a QQplot to compare a sample against the normal distribution, it doesn't give the user the ability to create QQplots for other distributions or to put testing bands on those plots.
-The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create QQplots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
-However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes.
+Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for Q-Q plots on real data.
+While the base-\proglang{R} package \pkg{stats} provides functionality for creating a Q-Q plot to compare a sample against the normal distribution, it doesn't give the user the ability to create Q-Q plots for other distributions or to put testing bands on those plots.
+The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
+Specifically, for the normal distribution \pkg{qqplotr} implements a simulation based method called tail sensitive (TS) testing bands, originally developed by Alder-Noiman \citep{aldor2013power}.
+However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes because it uses simulation.
 \newline
@@
 In section \hyperref[sec:examples]{4}, we introduce \pkg{qqconf} and demonstrate its functionality on a few multiple testing scenarios including including Type I error calibration and genetic studies.
-Finally, we conclude in section \hyperref[sec:discussion]{5} with a discussion of limitations the of ELL and \pkg{qqconf} as well as further directions for creating testing bands on QQplots.
+Finally, we conclude in section \hyperref[sec:discussion]{5} with a discussion of limitations the of ELL and \pkg{qqconf} as well as further directions for creating testing bands on Q-Q plots.
 \section{Methods}
@@
 \newline
-One of the main advantages of the local levels method compared to other global testing approaches, is that it can easily be used to put testing bands onto QQplots by simply graphing each $(h_{i}, g_{i})$ interval.
+One of the main advantages of the local levels method compared to other global testing approaches, is that it can easily be used to put testing bands onto Q-Q plots by simply graphing each $(h_{i}, g_{i})$ interval.
 This allows us to examine how a dataset might deviate from some null distribution much better than simply applying a test that yields a binary conclusion.
-Below, we present a few examples where a QQplot is useful, and where the local levels test seems ideal for assessing deviation from a global null hypothesis.
+Below, we present a few examples where a Q-Q plot is useful, and where the local levels test seems ideal for assessing deviation from a global null hypothesis.
 
@@
 
-Figure 3 shows the resulting QQplots for scenarios 1 (in blue) and 2 (in red), where the 45$^{\mbox{\footnotesize o}}$ line is shown as well as the testing bands obtained from the equal local levels procedure for testing, at global level .05, the null hypothesis that $p_1, \ldots, p_n$ have the same distribution as $n$ i.i.d.\ draws from Unif(0,1).
+Figure 3 shows the resulting Q-Q plots for scenarios 1 (in blue) and 2 (in red), where the 45$^{\mbox{\footnotesize o}}$ line is shown as well as the testing bands obtained from the equal local levels procedure for testing, at global level .05, the null hypothesis that $p_1, \ldots, p_n$ have the same distribution as $n$ i.i.d.\ draws from Unif(0,1).
 
@@
 \end{center}
-\caption{QQplot for Scenario 1 and Scenario 2 With Standard Axes.}
+\caption{Q-Q plot for Scenario 1 and Scenario 2 With Standard Axes.}
 \end{figure}
@@
 \end{center}
-\caption{QQplot for Scenario 1 and Scenario 2 With Axes On Log Scale.}
+\caption{Q-Q plot for Scenario 1 and Scenario 2 With Axes On Log Scale.}
 \end{figure}
@@
 \label{sec:methods}
-The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for QQplots.
+The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for Q-Q plots.
 Of course, our method is limited by the assumptions that (1) all of the tests are independent and that (2) all of the parameters of the null distribution are known.
-Currently, we are not aware of methods to handle the dependent case that allow for bands on QQplots.
+Currently, we are not aware of methods to handle the dependent case that allow for bands on Q-Q plots.
 To handle the second issue, Aldor-Noiman has adapted their method such that it will yield exact results when some parameters of the null distribution are unknown.

### 2021-04-26 article/manuscript.tex
pushed article updates

@@
 A number of methods have been created towards this end.
-Naively, one could put pointwise testing bands onto QQplots, which conduct $\alpha$ level tests on each order statistic of the sample.
+Naively, one could put pointwise testing bands onto Q-Q plots, which conduct $\alpha$ level tests on each order statistic of the sample.
 This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution.
 To appropriately deal with this multiple testing problem, the Komolgorov-Smirnov (KS) statistic is commonly used to create joint testing bands \citep{kolmogoroff1941confidence, smirnov1944approximate}.
-While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power}.
-A more promising approach, originally introduced by Berk and Jones and later developed by Gontscharuk et al., conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2016goodness}.
-Because this test, which will be referred to as equal local levels (ELL), conducts an $\eta$ level test on each order statistic, it is agnostic to any alternative distribution.
-This makes ELL a sensible choice for a standard test to use in creating testing bands on QQplots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
+While this method ensures the correct Type I error by using the distribution of the KS statistic to create joint testing bands, this test suffers from very low power under a variety of reasonable alternatives since it has low sensitivity to deviation in the tails of the null distribution \citep{aldor2013power, berk1979goodness}.
+A more promising approach would be to apply the equal local levels method (ELL) to create testing bands.
+This method, originally introduced by Berk and Jones and later developed by Gontscharuk et al.
+as an alternative testing procedure to higher-criticism and KS, conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness, gontscharuk2017asymptotics}.
+Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution.
+While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test to use in creating testing bands on Q-Q plots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
 \newline
 \newline
-Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for QQplots on real data.
-While the base-\proglang{R} package \pkg{stats} provides functionality for creating a QQplot to compare a sample against the normal distribution, it doesn't give the user the ability to create QQplots for other distributions or to put testing bands on those plots.
-The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create QQplots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
+Currently, there is no available software that allows a user to quickly create plausible and robust testing bands for Q-Q plots on real data.
+While the base-\proglang{R} package \pkg{stats} provides functionality for creating a Q-Q plot to compare a sample against the normal distribution, it doesn't give the user the ability to create Q-Q plots for other distributions or to put testing bands on those plots.
+The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
 However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes.
@@
 \newline
+%Add a line about Alder Noiman here where you mention tail sensitive and qqplotr
 In what follows, we introduce the \proglang{R} package \pkg{qqconf}.

### 2021-05-02 article/manuscript.tex
made article changes, fixed dparams bug in code

@@
 Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution.
-While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test to use in creating testing bands on Q-Q plots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
+While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test in this use case, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
 \newline
@@
 The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
-However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes.
+Specifically, for the normal distribution \pkg{qqplotr} implements a simulation based method called tail sensitive (TS) testing bands, originally developed by Alder-Noiman \citep{aldor2013power}.
+However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes because it uses simulation.
 \newline
 \newline
-%Add a line about Alder Noiman here where you mention tail sensitive and qqplotr
 In what follows, we introduce the \proglang{R} package \pkg{qqconf}.

### 2021-05-02 qqconf/R/qqplot.R

@@ -157,8 +157,8 @@ qq_conf_plot <- function(obs,
   exp.pts <- do.call(distribution, c(list(p=ppoints(samp.size, a=0)), dparams))
   if (log10 == TRUE) {
     exp.pts <- -log10(exp.pts)
-    low_exp_pt <- c * -log10(do.call(distribution, c(list(p=c(1 / max(samp.size * 1.25, samp.size + 2)))))) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * -log10(do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2)))))) + (1 - c) * exp.pts[samp.size]
+    low_exp_pt <- c * -log10(do.call(distribution, c(list(p=c(1 / max(samp.size * 1.25, samp.size + 2))), dparams))) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * -log10(do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2))), dparams))) + (1 - c) * exp.pts[samp.size]
     if (any(obs.pts <= 0)) {
       
       stop("log10 scaling can only be used with strictly positive distributions.")
@@ -168,8 +168,8 @@ qq_conf_plot <- function(obs,
   }
   else {
     
-    low_exp_pt <- c * do.call(distribution, c(list(p=c(1 / max(samp.size * 1.25, samp.size + 2))))) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2))))) + (1 - c) * exp.pts[samp.size]
+    low_exp_pt <- c * do.call(distribution, c(list(p=c(1 / max(samp.size * 1.25, samp.size + 2))), dparams)) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2))), dparams)) + (1 - c) * exp.pts[samp.size]
     
   }
   if (difference) {
@@ -240,7 +240,7 @@ qq_conf_plot <- function(obs,
       lines(exp.pts, pointwise.high, lty = pw.lty, col = pw.col, ...)
     }
   }
-  do.call(samples_func, c(list(x = exp.pts[2:(samp.size + 1)], y = y.pts, col = samples_col), ...))
[…]

### 2021-06-08 article/manuscript.Rnw

@@
 A number of methods have been created towards this end.
-Naively, one could put pointwise testing bands onto Q-Q plots, which conduct $\alpha$ level tests on each order statistic of the sample.
+Naively, one could put pointwise testing bands onto Q-Q plots, which conduct an $\alpha$ level test on each order statistic of the sample.
 This method is clearly insufficient, as it ignores the multiple testing problem and thus provides no guarantee on the Type I error rate of testing the global null hypothesis that all of the data come from the specified null distribution.
@@
 A more promising approach would be to apply the equal local levels method (ELL) to create testing bands.
-This method, originally introduced by Berk and Jones and later developed by Gontscharuk et al.
+This global testing method, originally introduced by Berk and Jones and later developed by Gontscharuk et al.
 as an alternative testing procedure to higher-criticism and KS, conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness, gontscharuk2017asymptotics}.
-Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution.
-While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test in this use case, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
+Previously, Alder-Noiman applied this method to create testing bands for Q-Q plots for the normal distribution using simulation \citep{aldor2013power}.
+Because this test conducts an $\eta$ level test on each order statistic and thus does not bias the user towards deviations of the sample from any particular part of the null distribution, we suggest it is a sensible choice for a standard method in creating testing bands for Q-Q plots.
 \newline
@@
 The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
-Specifically, for the normal distribution \pkg{qqplotr} implements a simulation based method called tail sensitive (TS) testing bands, originally developed by Alder-Noiman \citep{aldor2013power}.
-However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes because it uses simulation.
+Specifically, for the normal distribution \pkg{qqplotr} implements Alder-Noiman's simulation based method (which is referred to in the package as tail sensitive (TS) testing bands).
+However, this method does not provide testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes because it uses simulation.
 \newline
@@
 In section \hyperref[sec:examples]{4}, we introduce \pkg{qqconf} and demonstrate its functionality on a few multiple testing scenarios including including Type I error calibration and genetic studies.
-Finally, we conclude in section \hyperref[sec:discussion]{5} with a discussion of limitations the of ELL and \pkg{qqconf} as well as further directions for creating testing bands on Q-Q plots.
+Finally, we conclude in section \hyperref[sec:discussion]{5} with a discussion of some limitations of the ELL method and \pkg{qqconf} as well as further directions for creating testing bands on Q-Q plots.
 \section{Methods}
@@
 %
-This is known as ``equal local levels.''
+We refer to this as the ELL method, as mentioned in the Introduction.
 \newline
@@
 
+\subsection{Testing for Normality of Regression Residuals}
+When performing an ordinary least squares regression (OLS), it is common to assume that the error terms are idependentally drawn from a normal distribution.
+Specifically, suppose that we have $n$ observations $\{\mathbf{x_{i}}, y_{i}\}_{i=1}^{n}$, where each $y_{i}$ is a scalar and each $\mathbf{x_{i}}$ is a $1xp$ vector of regressors.
+Then, we model each $y_{i}$ as
+\begin{equation*}
+  y_{i} = \mathbf{x_{i}}^{T}\boldsymbol\beta + \epsilon_{i}
+\end{equation*}
+where $\mathbf{\boldsymbol\beta}$ is a $1xp$ vector of regression parameters to be estimated and we assume
+\begin{equation}
+  \epsilon_{1}, ..., \epsilon_{n} \distras{iid} N(0, \sigma^{2}).
+\end{equation}
+Once $\boldsymbol\beta$ and $\sigma^{2}$ are estimated (typically via maximum liklihood), for each $y_{i}$ we define the residual as 
+\begin{equation*}
+  r_{i} = \mathbf{x_{i}}^{T}\mathbf{\hat{\boldsymbol\beta}} - y_{i},
+\end{equation*}
+where $\hat{\boldsymbol\beta}$ is our estimate of $\boldsymbol\beta$.
+Then, we would like a Q-Q plot of the residuals with a Normal reference distribution to aid in testing assumption (4) above.
+Strictly speaking, even if assumption (4) is correct, the residuals are not independent because OLS leads to an estimation of $\hat{\boldsymbol\beta}$ such that $\sum_{i=1}^{n}r_{i} = 0$.
+However, accounting for the resulting negative correlation between the residuals when creating testing bands would be very difficult, and with a sufficiently large sample size this correlation becomes negligible.
+Thus, without an a priori reason to believe that the errors may deviate from normality at any particular point in the distribution, it makes sense to use ELL bands in this case.
+This is very easy to do with \pkg{qqconf}, as we show below.
+\newline
+\newline
+First, we generate data to perform a regression. Here, we will generate each $\epsilon_{i}$ independently from a $t(2.5)$ distribution. 
+%
+<<generate_datas>>=
+set.seed(100)
+n <- 100
+x <- runif(n)
+eta <- rt(n, df = 2.5)
+y <- x + eta
+@
+%
+Then, we fit a regression with the simulated data
+%
+<<fit_regression>>=
+reg <- lm(y ~ x)
+@
+%
+With \pkg{base}-\proglang{R} functionality, we can can create a qqplot using the function \code{qqnorm} and \code{qqline}. 
+%
+%
+<<base_qqplot, fig=TRUE>>=
+qqnorm(reg$residuals)
+qqline(reg$residuals)
+@
+%
+%
+\newline
+Clearly there's some indication of deviation in this plot, but it can be hard to tell how significant the deviation is without confidence bounds.
+With our function \code{qq_conf_plot}, it is much easier to be able to judge the significance of the deviation.
+%
+%
+<<qqconf_qqplot, fig=TRUE>>=
+library(qqconf)
+qq_conf_plot(
+  obs = reg$residuals,
+  samples_func = lines,
+  samples_col = "red"
+)
+@
+%
+%
+\newline
+Here, we can clearly see that in the right tail of the residuals goes beyond the normal testing bounds, giving strong evidence that the errors were not generated from a normal distribution.
+
 \subsection{Multiple Testing in Genome Wide Association Studies}
@@
 \section{Discussion}
-\label{sec:methods}
+\label{sec:discussion}
 The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for Q-Q plots.

### 2021-06-08 article/manuscript.tex

--- 2021-04-26 article/manuscript.tex
@@
 A more promising approach would be to apply the equal local levels method (ELL) to create testing bands.
-This method, originally introduced by Berk and Jones and later developed by Gontscharuk et al.
+This global testing method, originally introduced by Berk and Jones and later developed by Gontscharuk et al.
 as an alternative testing procedure to higher-criticism and KS, conducts a test with Type I error rate $\eta$ on each order statistic of the sample such that the Type I error rate of the global test is some desired level $\alpha$ \citep{berk1979goodness, gontscharuk2015intermediates, gontscharuk2016goodness, gontscharuk2017asymptotics}.
-Because this test conducts an $\eta$ level test on each order statistic, it can be used to create testing bands that are agnostic to any alternative distribution.
-While the ELL method has never previously been specifically applied to creating testing bands on Q-Q plots, we suggest it is a sensible choice for a standard test to use in creating testing bands on Q-Q plots, as it does not bias the user towards deviations of the sample in any particular part of the null distribution.
+Previously, Alder-Noiman applied this method to create testing bands for Q-Q plots for the normal distribution using simulation \citep{aldor2013power}.
+Because this test conducts an $\eta$ level test on each order statistic and thus does not bias the user towards deviations of the sample from any particular part of the null distribution, we suggest it is a sensible choice for a standard method in creating testing bands for Q-Q plots.
 \newline
@@
 The package \pkg{qqplotr} provides a number of helpful additions to the base-\proglang{R} functionality, including the ability to create Q-Q plots for a variety of reference distributions and a robust method for testing bands on the normal distribution \citep{qqplotr}.
-However, this package does not provide adequate testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes.
+Specifically, for the normal distribution \pkg{qqplotr} implements Alder-Noiman's simulation based method (which is referred to in the package as tail sensitive (TS) testing bands).
+However, this method does not provide testing bands for non-normal reference distributions and is not able to efficiently create testing bands for large sample sizes because it uses simulation.
 \newline
 \newline
-%Add a line about Alder Noiman here where you mention tail sensitive and qqplotr
 In what follows, we introduce the \proglang{R} package \pkg{qqconf}.
@@
 
+\subsection{Testing for Normality of Regression Residuals}
+When performing an ordinary least squares regression (OLS), it is common to assume that the error terms are idependentally drawn from a normal distribution.
+Specifically, suppose that we have $n$ observations $\{\mathbf{x_{i}}, y_{i}\}_{i=1}^{n}$, where each $y_{i}$ is a scalar and each $\mathbf{x_{i}}$ is a $1xp$ vector of regressors.
+Then, we model each $y_{i}$ as
+\begin{equation*}
+  y_{i} = \mathbf{x_{i}}^{T}\boldsymbol\beta + \epsilon_{i}
+\end{equation*}
+where $\mathbf{\boldsymbol\beta}$ is a $1xp$ vector of regression parameters to be estimated and we assume
+\begin{equation}
+  \epsilon_{1}, ..., \epsilon_{n} \distras{iid} N(0, \sigma^{2}).
+\end{equation}
+Once $\boldsymbol\beta$ and $\sigma^{2}$ are estimated (typically via maximum liklihood), for each $y_{i}$ we define the residual as 
+\begin{equation*}
+  r_{i} = \mathbf{x_{i}}^{T}\mathbf{\hat{\boldsymbol\beta}} - y_{i},
+\end{equation*}
+where $\hat{\boldsymbol\beta}$ is our estimate of $\boldsymbol\beta$.
+Then, we would like a Q-Q plot of the residuals with a Normal reference distribution to aid in testing assumption (4) above.
+Strictly speaking, even if assumption (4) is correct, the residuals are not independent because OLS leads to an estimation of $\hat{\boldsymbol\beta}$ such that $\sum_{i=1}^{n}r_{i} = 0$.
+However, accounting for the resulting negative correlation between the residuals when creating testing bands would be very difficult, and with a sufficiently large sample size this correlation becomes negligible.
+Thus, without an a priori reason to believe that the errors may deviate from normality at any particular point in the distribution, it makes sense to use ELL bands in this case.
+This is very easy to do with \pkg{qqconf}, as we show below.
+\newline
+\newline
+First, we generate data to perform a regression. Here, we will generate each $\epsilon_{i}$ independently from a $t(2.5)$ distribution. 
+%
+\begin{Schunk}
+\begin{Sinput}
+R> set.seed(100)
+R> n <- 100
+R> x <- runif(n)
+R> eta <- rt(n, df = 2.5)
+R> y <- x + eta
+\end{Sinput}
+\end{Schunk}
+%
+Then, we fit a regression with the simulated data
+%
+\begin{Schunk}
+\begin{Sinput}
+R> reg <- lm(y ~ x)
+\end{Sinput}
+\end{Schunk}
+%
+With \pkg{base}-\proglang{R} functionality, we can can create a qqplot using the function \code{qqnorm} and \code{qqline}. 
+%
+%
+\begin{Schunk}
+\begin{Sinput}
+R> qqnorm(reg$residuals)
+R> qqline(reg$residuals)
+\end{Sinput}
+\end{Schunk}
+\includegraphics{manuscript-base_qqplot}
+%
+%
+\newline
+Clearly there's some indication of deviation in this plot, but it can be hard to tell how significant the deviation is without confidence bounds.
+With our function \code{qq_conf_plot}, it is much easier to be able to judge the significance of the deviation.
+%
+%
+\begin{Schunk}
+\begin{Sinput}
+R> library(qqconf)
+R> qq_conf_plot(
++    obs = reg$residuals,
++    samples_func = lines,
++    samples_col = "red"
++  )
+\end{Sinput}
+\end{Schunk}
+\includegraphics{manuscript-qqconf_qqplot}
+%
+%
+\newline
+Here, we can clearly see that in the right tail of the residuals goes beyond the normal testing bounds, giving strong evidence that the errors were not generated from a normal distribution.
+
 \subsection{Multiple Testing in Genome Wide Association Studies}

### 2021-07-01 qqconf/R/ppplot.R
added misc updates to package

@@ -24,7 +24,9 @@
 #' positive distributions.
 #' @param add Whether to add points to an existing plot. 
 #' @param dparams List of additional parameters for the quantile function of the distribution
-#'   (e.g. df=1). For the uniform distribution, the default parameters are max = 1 and min = 0.
+#'   (e.g. df=1). Note that if any parameters of the distribution are specified, all other unspecified parameters of the distribution
+#'   will take on their default values. For the uniform distribution, parameter estimation is not supported, and
+#'   the default parameters are max = 1 and min = 0.
 #'   For other distributions parameters will be estimated if not provided and an appropriate estimation procedure exists.
 #'   For the normal distribution, we estimate the mean as the median and the standard deviation as \eqn{Sn} from the paper by Rousseeuw and Croux 1993
 #'   "Alternatives to the Median Absolute Deviation". For all other distributions besides uniform and normal,

### 2021-07-01 qqconf/R/qqplot.R

@@ -24,7 +24,9 @@
 #' positive distributions.
 #' @param add Whether to add points to an existing plot. 
 #' @param dparams List of additional parameters for the quantile function of the distribution
-#'   (e.g. df=1). For the uniform distribution, the default parameters are max = 1 and min = 0.
+#'   (e.g. df=1). Note that if any parameters of the distribution are specified, all other unspecified parameters of the distribution
+#'   will take on their default values. For the uniform distribution, parameter estimation is not supported, and
+#'   the default parameters are max = 1 and min = 0.
 #'   For other distributions parameters will be estimated if not provided and an appropriate estimation procedure exists.
 #'   For the normal distribution, we estimate the mean as the median and the standard deviation as \eqn{Sn} from the paper by Rousseeuw and Croux 1993
 #'   "Alternatives to the Median Absolute Deviation". For all other distributions besides uniform and normal,
@@ -200,7 +202,7 @@ qq_conf_plot <- function(obs,
     high_exp_pt <- c * -log10(do.call(distribution, c(list(p=1 - c(1 / max(samp.size * 1.25, samp.size + 2))), dparams))) + (1 - c) * exp.pts[samp.size]
     if (any(obs.pts <= 0)) {
       
-      stop("log10 scaling can only be used with strictly positive distributions.")
+      stop("log10 scaling can only be used with strictly positive distributions. Consider using pp_conf_plot.")
       
     }
     obs.pts <- -log10(obs.pts)

### 2021-07-01 qqconf/src/qqconf_init.c
added init for c code

@@ -1,0 +1,20 @@
+#include <stdlib.h> // for NULL
+#include <R_ext/Rdynload.h>
+
+/* FIXME: 
+   Check these declarations against the C/Fortran source code.
+*/
+
+/* .C calls */
+extern void jointlevel_twosided(void *, void *, void *, void *);
+
+static const R_CMethodDef CEntries[] = {
+    {"jointlevel_twosided", (DL_FUNC) &jointlevel_twosided, 4},
+    {NULL, NULL, 0}
+};
+
+void R_init_qqconf(DllInfo *dll)
+{
+    R_registerRoutines(dll, CEntries, NULL, NULL, NULL);
+    R_useDynamicSymbols(dll, FALSE);
+}

### 2021-07-03 article/manuscript.Rnw
made updates to api

@@
   alpha = .05,
-  samples_func = lines,
-  samples_col = "red"
+  points_params = list(col="red", type="l")
 )
@@
   alpha = .05,
-  samples_func = lines,
-  samples_col = "red",
+  points_params = list(col="red", type="l"),
   log10 = TRUE
@@
   obs = reg$residuals,
-  samples_func = lines,
-  samples_col = "red"
+  points_params = list(col="red")
 )

### 2021-07-03 article/manuscript.tex
made updates to api

@@
 +    alpha = .05,
-+    samples_func = lines,
-+    samples_col = "red"
++    points_params = list(col="red", type="l")
 +  )
@@
 +    alpha = .05,
-+    samples_func = lines,
-+    samples_col = "red",
++    points_params = list(col="red", type="l"),
 +    log10 = TRUE
@@
 +    obs = reg$residuals,
-+    samples_func = lines,
-+    samples_col = "red"
++    points_params = list(col="red")
 +  )

### 2021-07-03 qqconf/R/qqplot.R
fixed line error

@@ -311,6 +311,14 @@ qq_conf_plot <- function(obs,
     }
   }
   do.call(points, c(list(x = exp.pts[2:(samp.size + 1)], y = y.pts), points_params))
-  do.call(lines, c(list(x = c(min(exp.pts), max(exp.pts)), y = c(min(y.pts), max(y.pts))), line_params))
+  if (difference) {
+    
+    do.call(lines, c(list(x = c(min(exp.pts), max(exp.pts)), y = c(0, 0)), line_params))
+    
+  } else{
+    
+    do.call(lines, c(list(x = c(min(exp.pts), max(exp.pts)), y = c(min(exp.pts), max(exp.pts))), line_params))
+    
+  }
   
 }

### 2021-07-03 qqconf/R/ppplot.R
added line fix to pp plot code

@@ -307,6 +307,14 @@ pp_conf_plot <- function(obs,
     }
   }
   do.call(points, c(list(x = exp.pts[2:(samp.size + 1)], y = y.pts), points_params))
-  do.call(lines, c(list(x = c(min(exp.pts), max(exp.pts)), y = c(min(y.pts), max(y.pts))), line_params))
+  if (difference) {
+    
+    do.call(lines, c(list(x = c(min(exp.pts), max(exp.pts)), y = c(0, 0)), line_params))
+    
+  } else{
+    
+    do.call(lines, c(list(x = c(min(exp.pts), max(exp.pts)), y = c(min(exp.pts), max(exp.pts))), line_params))
+    
+  }
   
 }

### 2021-07-03 qqconf/R/ppplot.R
fixed examples for pp plot

@@ -59,21 +59,21 @@
 #' # Make same plot on -log10 scale to highlight small p-values
 #' pp_conf_plot(
 #'   obs=smp, 
-#'   distribution = punif,
+#'   distribution = pnorm,
 #'   log10 = TRUE
 #' )
 #' 
 #' # Make same plot with difference between observed and expected values on the y-axis 
 #' pp_conf_plot(
 #'   obs=smp, 
-#'   distribution = punif,
+#'   distribution = pnorm,
 #'   difference = TRUE
 #' )
 #' 
 #' # Make same plot with samples plotted as a blue line and expected value line plotted as a red line
 #' pp_conf_plot(
 #'   obs=smp, 
-#'   distribution = punif,
+#'   distribution = pnorm,
 #'   plot_pointwise = TRUE,
 #'   method = "ell",
 #'   points_params = list(col="blue", type="l"),

### 2021-07-03 qqconf/R/ppplot.R
fixed log10 error with ppplot

@@ -194,10 +194,12 @@ pp_conf_plot <- function(obs,
   obs.pts <- do.call(distribution, c(list(q=sort(obs)), dparams))
   exp.pts <- ppoints(samp.size, a=0)
   if (log10 == TRUE) {
+    
     exp.pts <- -log10(exp.pts)
-    low_exp_pt <- c * -log10(do.call(distribution, c(list(q=c(1 / max(samp.size * 1.25, samp.size + 2))), dparams))) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * -log10(do.call(distribution, c(list(q=1 - c(1 / max(samp.size * 1.25, samp.size + 2))), dparams))) + (1 - c) * exp.pts[samp.size]
+    low_exp_pt <- c * -log10(1 / max(samp.size * 1.25, samp.size + 2)) + (1 - c) * exp.pts[1]
+    high_exp_pt <- c * -log10(1 - (1 / max(samp.size * 1.25, samp.size + 2))) + (1 - c) * exp.pts[samp.size]
     obs.pts <- -log10(obs.pts)
+    
   }
   else {
     

### 2021-07-03 qqconf/R/ppplot.R
extended region out to 0 and 1 for the ppplot, doesn't look great

@@ -203,8 +203,10 @@ pp_conf_plot <- function(obs,
   }
   else {
     
-    low_exp_pt <- c * (1 / max(samp.size * 1.25, samp.size + 2)) + (1 - c) * exp.pts[1]
-    high_exp_pt <- c * (1 - (1 / max(samp.size * 1.25, samp.size + 2))) + (1 - c) * exp.pts[samp.size]
+    #low_exp_pt <- c * (1 / max(samp.size * 1.25, samp.size + 2)) + (1 - c) * exp.pts[1]
+    #high_exp_pt <- c * (1 - (1 / max(samp.size * 1.25, samp.size + 2))) + (1 - c) * exp.pts[samp.size]
+    low_exp_pt <- 0
+    high_exp_pt <- 1
 
   }
   if (difference) {
@@ -256,13 +258,6 @@ pp_conf_plot <- function(obs,
       global.high <- -log10(global.high)
     }
     
-    # code to extend region for visibility
-    global.low <- c(global.low[1], global.low, global.low[samp.size])
-    global.high <- c(global.high[1], global.high, global.high[samp.size])
-    pointwise.low <- c(pointwise.low[1], pointwise.low, pointwise.low[samp.size])
-    pointwise.high <- c(pointwise.high[1], pointwise.high, pointwise.high[samp.size])
-    exp.pts <- c(low_exp_pt, exp.pts, high_exp_pt)
-    
     if ("ylim" %in% names(dots)) {
       
       bottom <- dots$ylim[1] - 1000
@@ -278,20 +273,38 @@ pp_conf_plot <- function(obs,
     }
     
     if (difference) {
+      
+      global_low_diff <- global.low - exp.pts
+      global_high_diff <- global.high - exp.pts
+      pointwise_low_diff <- pointwise.low - exp.pts
+      pointwise_high_diff <- pointwise.high - exp.pts
+      exp.pts <- c(low_exp_pt, exp.pts, high_exp_pt)
+      global_low_diff <- c(global_low_diff[1], global_low_diff, global_low_diff[samp.size])
+      global_high_diff <- c(global_high_diff[1], global_high_diff, global_high_diff[samp.size])
+      pointwise_low_diff <- c(pointwise_low_diff[1], pointwise_low_diff, pointwise_low_diff[samp.size])
+      pointwise_high_diff <- c(pointwise_high_diff[1], pointwise_high_diff, pointwise_high_diff[samp.size])
+      
[…]

### 2021-07-03 qqconf/R/ppplot.R
removed unneccessary comments in ppplot code

@@ -226,21 +226,13 @@ pp_conf_plot <- function(obs,
     
     global.bounds <- do.call(get_bounds_two_sided,
                              c(list(alpha = alpha, n = samp.size), bounds_params))
-    # Here, have to figure out how to do this for the KS test
-    # I don't think that this should be too hard, but I'm not completely sure
+
     if (method == "ell") {
       
       global.low <- global.bounds$lower_bound
       global.high <- global.bounds$upper_bound
       
     } else if (method == "ks") {
-      
-      #probs <- ppoints(samp.size)
-      #epsilon <- sqrt((1 / (2 * samp.size)) * log(2 / (1 - conf.int)))
-      #lp <- pmax(probs - epsilon, rep(0, samp.size))
-      #up <- pmin(probs + epsilon, rep(1, samp.size))
-      #global.low <- do.call(distribution, c(list(q = lp), dparams))
-      #global.high <- do.call(distribution, c(list(q = up), dparams))
       
       probs <- ppoints(samp.size)
       epsilon <- sqrt((1 / (2 * samp.size)) * log(2 / (1 - conf.int)))

### 2021-07-03 qqconf/R/ppplot.R
fixed first example mistake in ppplot

@@ -53,7 +53,7 @@
 #' # Plot PP plot against normal distribution with mean and variance estimated
 #' pp_conf_plot(
 #'   obs=smp, 
-#'   distribution = punif
+#'   distribution = pnorm
 #' )
 #' 
 #' # Make same plot on -log10 scale to highlight small p-values

### 2021-07-04 article/manuscript.Rnw
updated manuscript

@@
 
-% It may also make sense for me to make a comparison to the Kolmogorov-Smirnov statistic at some point. I should probably include some instructive graphs or something.
-% I want to have a different paragraph to better introduce the concept
-% This shouldn't be too difficult
 Suppose we have devised a new testing procedure to test a null hypothesis $H_{0}$ with test statistic $T$, where we also specify a particular method to calculate or approximate p-values.
@@
 In Step 3, one could use many different testing bands.
-However, in the calibration of p-values, we typically don't have the expectation that our p-values would be more likely to deviate from uniform in any particular region, and so it makes sense to use the local levels test because it is agnostic to the alternative distribution.
-Moreover, since it is generally most concerning if small p-values are not calibrated, i.e.
-those in the lower tail of the uniform distribution, the local levels test is preferable to the standard KS test because it is much more sensitive in the tails (Aldor-Noiman 2013).
+However, in the calibration of p-values, we typically don't have the expectation that our p-values would be more likely to deviate from uniform in any particular region, and so it makes sense to use the local levels test because it is agnostic to the space of alternative distribution.
+Moreover, since it is generally most concerning if small p-values are not calibrated (i.e.
+those in the lower tail of the uniform distribution), the local levels test is preferable to the standard KS test because it is much more sensitive in the tails (Aldor-Noiman 2013).
 
@@
 \end{center}
-\caption{Q-Q plot for Scenario 1 and Scenario 2 With Standard Axes.}
+\caption{QQ plot for Scenario 1 and Scenario 2 With Standard Axes.}
 \end{figure}
@@
 \end{center}
-\caption{Q-Q plot for Scenario 1 and Scenario 2 With Axes On Log Scale.}
+\caption{QQ plot for Scenario 1 and Scenario 2 With Axes On Log Scale.}
 \end{figure}
@@
 \newline
-First, we generate data to perform a regression. Here, we will generate each $\epsilon_{i}$ independently from a $t(2.5)$ distribution. 
-%
-<<generate_datas>>=
-set.seed(100)
+First, we generate data to perform a regression. Here, we will generate each $\epsilon_{i}$ independently from a $t(3)$ distribution.
+
+<<generate_data>>=
+set.seed(20)
 n <- 100
 x <- runif(n)
-eta <- rt(n, df = 2.5)
+eta <- rt(n, df = 3)
 y <- x + eta
 @
-%
+
 Then, we fit a regression with the simulated data
-%
+
 <<fit_regression>>=
@@
 @
-%
+
 With \pkg{base}-\proglang{R} functionality, we can can create a qqplot using the function \code{qqnorm} and \code{qqline}.
-%
-%
-<<base_qqplot, fig=TRUE>>=
+
+<<base_qqplot, fig=TRUE, include=FALSE>>=
 qqnorm(reg$residuals)
@@
 @
-%
-%
-\newline
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-base_qqplot}
+\end{center}
+\caption{QQ Plot for Regression Residuals with Base R Functionality}
+\end{figure}
+
 Clearly there's some indication of deviation in this plot, but it can be hard to tell how significant the deviation is without confidence bounds.
 With our function \code{qq_conf_plot}, it is much easier to be able to judge the significance of the deviation.
-%
-%
-<<qqconf_qqplot, fig=TRUE>>=
+
+<<qqconf_qqplot, fig=TRUE, include=FALSE>>=
 library(qqconf)
@@
   obs = reg$residuals,
-  points_params = list(col="red")
+  points_params = list(col="blue", pch = 20, cex = .5)
 )
 @
-%
-%
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-qqconf_qqplot}
+\end{center}
+\caption{QQ Plot for Regression Residuals with ELL Bounds}
+\end{figure}
+
+Here, we can clearly see that both the left and right tail of the residuals goes beyond the normal testing bounds, giving strong evidence that the errors were not generated from a normal distribution.
 \newline
-Here, we can clearly see that in the right tail of the residuals goes beyond the normal testing bounds, giving strong evidence that the errors were not generated from a normal distribution.
+\newline
+This example also highlights an instance in which the ELL method is preferable to KS.
+Because KS is much more sensitive to deviations in the center of the distribution than it is to deviations in the tails of the distribution, it does not yeild a rejection of the null hypothesis in this case (Figure 7).
+We can generate KS bounds by simply setting the \code{method} arguments to \code{"ks"} in the \code{qq_conf_plot} function.
+
+<<qqconf_qqplot_ks, fig=TRUE, include=FALSE>>=
+library(qqconf)
+qq_conf_plot(
+  obs = reg$residuals,
+  method = "ks",
+  points_params = list(col="blue", pch = 20, cex = .5)
+)
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-qqconf_qqplot_ks}
+\end{center}
+\caption{QQ Plot for Regression Residuals with KS Bounds}
+\end{figure}
 
 \subsection{Multiple Testing in Genome Wide Association Studies}
+\subsubsection{Applicability of Equal Local Levels to Genome Wide Association Studies}
 In genome wide association studies (GWAS), we are interested in identifying the genetic variants that are responsible for biological traits.
@@
 While the SNPs have a local correlation structure, this has only a weak effect at a genome-wide scale.
-Thus, the local levels procedure still provides a valuable visualization tool to assess the extent and type of any deviation from the null, even though it is not exact.
+Thus, the local levels procedure still provides a valuable visualization tool to assess the extent and type of deviation from the null, even though it is not exact.
 Particularly in genetics, if the p-values deviate from the null, it can be very useful to view graphically how they deviate.
-For instance, if there are a few very large p-values but the rest of the distribution looks relatively uniform, then this indicates that the trait of interest is driven by a few mutations.
-If, however, there are some small deviations throughout the p-value distribution, then this indicates that trait of interest is driven by a number of genes that all play some small part in a complex biological process, or potentially by some confounding variables that are not controlled for.
+For instance, if a few tests yield very small p-values but the p-values from the rest of the tests looks relatively uniform, this indicates that the trait of interest is likely driven by a few mutations.
+If, however, there are some small deviations throughout the p-value distribution, this indicates that trait of interest is likely driven by a number of genes that all play some small part in a complex biological process, or potentially by some confounding variables that are not controlled for.
 \newline
@@
 If a very specific distribution for $H_{A}$ is suspected, then it makes sense to use a test that has high power under this alternative, which may not be our local levels test.
-However, in the general case when little is known about the alternative distribution, using local levels is desirable because it is agnostic to alternative distributions.
-Moreover, since small p-values are often of great interest in GWAS because they can indicate the main biological drivers of a trait, the local levels test is far superior to the KS test due to its tail sensitivity.
-%Here is where the biological example goes with the code. I want to have the graphs that I make from this and then I also want
+However, in the general case when little is known about the alternative distribution, using local levels is desirable because it is agnostic to the space of alternative distributions.
+Moreover, since small p-values are often of great interest in GWAS because they can indicate the main biological drivers of a trait, the local levels test is far superior to the KS test due to its comparative tail sensitivity.
+\subsubsection{Appliction of Equal Local Levels to Creutzfeld-Jakob Disease}
+We downloaded the p-values from a GWAS of Creutzfeld-Jakob disease in a sample of XXX cases and YYY controls.
+The GWAS found strong genetic associations on chromosomes A and B.
+Here, we remove those chromosomes from the results in order to display the p-values from tests that are not obviously from a non-uniform distribution.
+To more clearly allow for display of the individual p-values, we downsample the number of tests to 10,000 by extracting approximately equally spaced genetic markers.
+<<load_data>>=
+cjd_df <- read.table("data/cjd_sample.txt", header = TRUE)
+@
+We then make QQ plots of these 10,000 tests with 95\% testing bands. First, we make a standard QQ plot of observed quantiles versus expected quantiles (Figure 8).
+<<cjd_standard_qq, fig=TRUE, include=FALSE>>=
+library(qqconf)
+qq_conf_plot(
+  obs = cjd_df[,3],
+  distribution = qunif,
+  points_params = list(pch = 21, cex = 0.2)
+  )
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.5]{manuscript-cjd_standard_qq}
+\end{center}
+\caption{Standard QQ Plot for CJD GWAS p-values}
+\end{figure}
+
+Unfortunately, this plot results in deviations from the expected line that are difficult to see.
+To aid visualization, we also plot the deviation of the observed quantiles from the expected quantiles versus the expected quantiles (Figure 9).
+This can be done easily by setting the \code{difference} parameter to \code{TRUE} in \code{qq_conf_plot}.
+<<cjd_diff_qq, fig=TRUE, include=FALSE>>=
+qq_conf_plot(
+  obs = cjd_df[,3],
+  distribution = qunif,
+  points_params = list(pch = 21, cex = 0.2),
+  difference = TRUE
+  )
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.5]{manuscript-cjd_diff_qq}
+\end{center}
+\caption{QQ Plot With y-axis as Observed - Expected Quantile for CJD GWAS p-values}
+\end{figure}
+
+This plot is much easier to interpret, but note that tests in which there is an association will result in small p-values, which will be difficult to see when the plot axes are on the 0 to 1 scale.
+To see the small p-values we repeat the plots but with the axes on the -log10 scale (Figures 10 and 11).
+This can be done by setting the \code{log10} parameter of \code{qqconf} to \code{TRUE}
+
+<<cjd_log_qq, fig=TRUE, include=FALSE>>=
+qq_conf_plot(
+  obs = cjd_df[,3],
+  distribution = qunif,
+  points_params = list(pch = 21, cex = 0.2),
+  log10 = TRUE
+  )
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.5]{manuscript-cjd_log_qq}
+\end{center}
+\caption{QQ Plot With y-axis as -$\textrm{log}_{10}$(Observed Quantile) for CJD GWAS p-values}
+\end{figure}
+
+<<cjd_log_diff_qq, fig=TRUE, include=FALSE>>=
+qq_conf_plot(
+  obs = cjd_df[,3],
+  distribution = qunif,
+  points_params = list(pch = 21, cex = 0.2),
+  difference = TRUE,
+  log10 = TRUE,
+  ylim = c(-0.2, 1.1)
+  )
+@
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-cjd_log_diff_qq}
+\end{center}
+\caption{QQ Plot With y-axis as -$\textrm{log}_{10}$(Observed Quantile) + $\textrm{log}_{10}$(Expected Quantile) for CJD GWAS p-values}
+\end{figure}
+
 \section{Discussion}
 \label{sec:discussion}
-The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for Q-Q plots.
+The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for QQ plots.
 Of course, our method is limited by the assumptions that (1) all of the tests are independent and that (2) all of the parameters of the null distribution are known.
-Currently, we are not aware of methods to handle the dependent case that allow for bands on Q-Q plots.
-To handle the second issue, Aldor-Noiman has adapted their method such that it will yield exact results when some parameters of the null distribution are unknown.
-However, if the dataset is very large, Aldor-Noiman's method is prohibitively slow.
+Currently, we are not aware of methods to handle the dependent case that allow for bands on QQ plots.
+To handle the issue of parameter uncertainty, Aldor-Noiman has adapted their method such that it will yield exact results when some parameters of the null distribution are unknown.
+However, if the dataset is very large, Aldor-Noiman's method is prohibitively slow because it uses simulation.
 In this case, we suggest that our method be used because it is much faster, and with a sufficiently large dataset the uncertainty in the parameters will become negligible under standard regularity conditions.
-Methods to handle parameter uncertainty with an exact calculation have been discussed in the context of the normal distribution \citep{rosenkrantz2000confidence}, but a general method towards this end has not been developed, and would be an important next step.
+Methods to handle parameter uncertainty with an exact calculation (as opposed to simulation) have been discussed in the context of the normal distribution \citep{rosenkrantz2000confidence}, but a general method towards this end has not been developed, and would be an important next step.
 \newline
@@
 Our software is available on CRAN.
-To aid in computation speed, we have pre-computed a number of different local level values given a global level and the size of the dataset.
-This computes the testing bands very quickly with little error.
-We have also implemented a one-sided test for the case in which we are only concerned with values that are smaller than would be expected under the null (e.g.
-we only care about small p-values).
+In addition to the QQ plot functionality, we've implemented PP plots using the same methodology and a very similar interface.
+We've also provided functionality to directly calculate ELL bounds given a sample size $n$ and a global level $\alpha$.
+For more information on these functions, please see the code documentation.
 

### 2021-07-05 qqconf/R/ppplot.R
updated pp and qq plot documentation up to Mary Sara's comments

@@ -7,37 +7,37 @@
 #' If any of the points of the pp-plot fall outside the simultaneous acceptance region for the selected
 #' level alpha test, that means that we can reject the null hypothesis that the data are i.i.d. draws from the
 #' specified distribution. If \code{difference} is set to TRUE, the vertical axis plots the 
-#' observed quantile minus expected quantile. If pointwise bands are used, then on average, alpha * n of the points will fall outside
+#' observed quantile minus expected quantile. If pointwise bounds are used, then on average, alpha * n of the points will fall outside
 #' the bounds under the null hypothesis, so the chance that the pp-plot has any points falling outside of the pointwise bounds
 #' is typically much higher than alpha under the null hypothesis. For this reason, a simultaneous region is preferred. 
 #' 
 #' @param obs The observed data.
 #' @param distribution The probability function for the specified distribution. Defaults to qnorm.
-#' Custom distributions are allowed so long as all parameters are supplied in dparams.
+#' Custom distributions are allowed as long as all parameters are supplied in dparams.
 #' @param method Method for simultaneous testing bands. Must be either "ell" (equal local levels test), which applies a level \eqn{\eta} pointwise
-#' test to each order statistic such that the Type I error of the global test is \eqn{\alpha}, or "ks" to apply a 
-#' Kolmogorov-Smirnov test. For \eqn{\alpha} = .01, .05, and .1, "ell" is recommended.
+#' test to each order statistic such that the Type I error of the global test is \code{alpha}, or "ks" to apply a 
+#' Kolmogorov-Smirnov test. For \code{alpha} = .01, .05, and .1, "ell" is recommended.
 #' @param alpha Type I error of global test of whether the data come from the reference distribution.
 #' @param difference Whether to plot the difference between the observed and
 #'   expected values on the vertical axis.
-#' @param log10 Whether to plot axes on -log10 scale (e.g. to see small p-values). Can only be used for strictly
-#' positive distributions.
+#' @param log10 Whether to plot axes on -log10 scale (e.g. to see small p-values). 
 #' @param add Whether to add points to an existing plot. 
 #' @param dparams List of additional parameters for the quantile function of the distribution
-#'   (e.g. df=1). Note that if any parameters of the distribution are specified, all other unspecified parameters of the distribution
-#'   will take on their default values. For the uniform distribution, parameter estimation is not supported, and
[…]

### 2021-07-05 qqconf/R/qqplot.R

@@ -7,16 +7,16 @@
 #' If any of the points of the qq-plot fall outside the simultaneous acceptance region for the selected
 #' level alpha test, that means that we can reject the null hypothesis that the data are i.i.d. draws from the
 #' specified distribution. If \code{difference} is set to TRUE, the vertical axis plots the 
-#' observed quantile minus expected quantile. If pointwise bands are used, then on average, alpha * n of the points will fall outside
+#' observed quantile minus expected quantile. If pointwise bounds are used, then on average, alpha * n of the points will fall outside
 #' the bounds under the null hypothesis, so the chance that the qq-plot has any points falling outside of the pointwise bounds
 #' is typically much higher than alpha under the null hypothesis. For this reason, a simultaneous region is preferred. 
 #' 
 #' @param obs The observed data.
 #' @param distribution The quantile function for the specified distribution. Defaults to qnorm.
-#' Custom distributions are allowed so long as all parameters are supplied in dparams.
+#' Custom distributions are allowed as long as all parameters are supplied in dparams.
 #' @param method Method for simultaneous testing bands. Must be either "ell" (equal local levels test), which applies a level \eqn{\eta} pointwise
-#' test to each order statistic such that the Type I error of the global test is \eqn{\alpha}, or "ks" to apply a 
-#' Kolmogorov-Smirnov test. For \eqn{\alpha} = .01, .05, and .1, "ell" is recommended.
+#' test to each order statistic such that the Type I error of the global test is \code{alpha}, or "ks" to apply a 
+#' Kolmogorov-Smirnov test. For \code{alpha} = .01, .05, and .1, "ell" is recommended.
 #' @param alpha Type I error of global test of whether the data come from the reference distribution.
 #' @param difference Whether to plot the difference between the observed and
 #'   expected values on the vertical axis.
@@ -24,20 +24,21 @@
 #' positive distributions.
 #' @param add Whether to add points to an existing plot. 
 #' @param dparams List of additional parameters for the quantile function of the distribution
-#'   (e.g. df=1). Note that if any parameters of the distribution are specified, all other unspecified parameters of the distribution
-#'   will take on their default values. For the uniform distribution, parameter estimation is not supported, and
+#'   (e.g. df=1). Note that if any parameters of the distribution are specified, parameter estimation will not be performed
[…]

### 2021-07-08 article/manuscript.Rnw
updated neuro citation

@@
 \subsubsection{Appliction of Equal Local Levels to Creutzfeld-Jakob Disease}
-We downloaded the p-values from a GWAS of Creutzfeld-Jakob disease in a sample of XXX cases and YYY controls.
-The GWAS found strong genetic associations on chromosomes A and B.
+We downloaded the p-values from a GWAS of Creutzfeld-Jakob disease in a sample of 4110 cases and 13,569 controls \citep{jones2020identification}.
+Test of association between risk for the disease and genetic variants was done at 6,314,492 SNPs.
+Major genetic risk loci were found on chromosomes 1 and 20.
 Here, we remove those chromosomes from the results in order to display the p-values from tests that are not obviously from a non-uniform distribution.
-To more clearly allow for display of the individual p-values, we downsample the number of tests to 10,000 by extracting approximately equally spaced genetic markers.
+For display purposes, we subsample the remaining SNPs to 10,000 approximately evenly spaced SNPs.
+Subsampling helps ensure that correlations between SNPs that are located
+near each other is minimized.
 <<load_data>>=
@@
 
+From the QQ plots, we can see that there is an excess of small p-values, indicating that the test statistics do not follow the expected null distribution.
+
 \section{Discussion}

### 2021-07-08 qqconf/R/ppplot.R
added right tail option

@@ -21,6 +21,12 @@
 #' @param difference Whether to plot the difference between the observed and
 #'   expected values on the vertical axis.
 #' @param log10 Whether to plot axes on -log10 scale (e.g. to see small p-values). 
+#' @param right_tail This parameter is only used if \code{log10} is \code{TRUE}. When \code{TRUE},
+#' the x-axis is -log10(1 - Expected Probability) and the y-axis is -log10(1 - Observed Probability).
+#' When \code{FALSE} (default) the x-axis is -log10(Expected Probability) and the y-axis is 
+#' -log10(Observed Probability). The parameter should be set to \code{TRUE} to make
+#' observations in the right tail of the distribution easier to see, and set to false to make the 
+#' observations in the left tail of the distribution easier to see.
 #' @param add Whether to add points to an existing plot. 
 #' @param dparams List of additional parameters for the quantile function of the distribution
 #'   (e.g. df=1). Note that if any parameters of the distribution are specified, parameter estimation will not be performed
@@ -90,6 +96,7 @@ pp_conf_plot <- function(obs,
                          alpha = 0.05,
                          difference = FALSE,
                          log10 = FALSE,
+                         right_tail = FALSE,
                          add = FALSE,
                          dparams = list(),
                          bounds_params = list(),
@@ -162,11 +169,15 @@ pp_conf_plot <- function(obs,
   
   dots <- list(...)
   method <- match.arg(method)
-  if ( is.null(dots$ylab)) {
-    if (difference && log10) {
+  if (is.null(dots$ylab)) {
+    if (difference && log10 && right_tail) {
+      ylab <- expression("-log"[10]*"(1 - Observed probabilities) + log"[10]*"(1 - Expected probabilities)")
+    } else if (difference && log10) {
       ylab <- expression("-log"[10]*"(Observed probabilities) + log"[10]*"(Expected probabilities)")
     } else if(difference) {
       ylab <- 'Obseved probabilities - Expected probabilities'
+    } else if (log10 && right_tail) {
+      ylab <- expression("-log"[10]*"(1 - Observed probabilities)")
     } else if (log10) {
[…]

### 2021-07-10 qqconf/R/qqplot.R
added code for speedup in ELL case

@@ -65,7 +65,7 @@
 #' qq_conf_plot(
 #'   obs=smp, 
 #'   distribution = qunif,
-#'   points_params = list(cex = .5)
+#'   points_params = list(cex = .5),
 #'   log10 = TRUE
 #' )
 #' 

### 2021-07-10 qqconf/src/jointlevel_two_sided_ell_speedup.c

@@ -2,14 +2,16 @@
 #define MIN(X, Y) (((X) < (Y)) ? (X) : (Y))
 #define MAX(X, Y) (((X) > (Y)) ? (X) : (Y))
 
+#include <stdio.h>
 #include <math.h>
 #include <stdlib.h>
 #include <R.h>
 #include <Rinternals.h>
 
 // Calculate global level associated with bounds given in b_vec
-// Parameter bound_id indicates if bound is upper or lower 
-void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *out) {
+// Parameter bound_id indicates if bound is upper or lower
+// Uses speedup for equal local levels case 
+void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_points, double *out) {
 
   int n = *num_points;
   double *b_vec_prev;
@@ -19,11 +21,11 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
   lgamma_arr[0] = 0;
   lgamma_arr[1] = 0;
   for(int i = 2; i <= (n + 1); i = i + 1) {
-    
-    lgamma_arr[i] = lgamma_arr[i - 1] + log(i - 1);
-    
+
+      lgamma_arr[i] = lgamma_arr[i - 1] + log(i - 1);
+
   }
-  
+
   b_vec_prev = (double *) malloc((n + 1) * sizeof(double));
   b_vec_prev[0] = pow((1 - b_vec[0]), n);
 
@@ -35,9 +37,7 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
   int l_lower = 0;
   int l_upper = 0;
 
-  int l_loop_upper_bound = 0;
-
-  for(int k = 1; k <= (2 * n - 1); k = k + 1) {
+  for(int k = 1; k <= n; k = k + 1) {
 
     l_lower = j_lower;
     l_upper = j_upper;
@@ -58,7 +58,7 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
     for(int j = j_lower; j <= j_upper; j = j + 1) {
 
       b_vec_next[j] = 0; // initialize the probability value
-      l_loop_upper_bound = MIN(l_upper, j);
+      int l_loop_upper_bound = MIN(l_upper, j);
 
[…]

### 2021-07-11 qqconf/src/jointlevel_two_sided.c
added src before branch switch

@@ -11,9 +11,11 @@
 // Parameter bound_id indicates if bound is upper or lower 
 void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *out) {
 
+  Rprintf("log(1) = %d\n", log(1));
   int n = *num_points;
   double *b_vec_prev;
   double *lgamma_arr;
+  Rprintf("log(1) = %d\n", log(1));
   // Pre-compute vector of lgamma values to avoid repeat computation
   lgamma_arr = (double *) malloc((n + 2) * sizeof(double));
   lgamma_arr[0] = 0;
@@ -23,6 +25,8 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
     lgamma_arr[i] = lgamma_arr[i - 1] + log(i - 1);
     
   }
+  
+  Rprintf("log(1) = %d\n", log(1));
   
   b_vec_prev = (double *) malloc((n + 1) * sizeof(double));
   b_vec_prev[0] = pow((1 - b_vec[0]), n);
@@ -75,6 +79,7 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
 
   }
 
+  Rprintf("log(1) = %d\n", log(1));
   *out = b_vec_prev[n];
   free(b_vec_prev);
   free(b_vec_next);

### 2021-07-11 qqconf/src/jointlevel_two_sided_ell_speedup.c

@@ -13,18 +13,34 @@
 // Uses speedup for equal local levels case 
 void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_points, double *out) {
 
+  Rprintf("log(1) = %d\n", log(1));
   int n = *num_points;
   double *b_vec_prev;
   double *lgamma_arr;
+  Rprintf("log(1) = %d\n", log(1));
   // Pre-compute vector of lgamma values to avoid repeat computation
   lgamma_arr = (double *) malloc((n + 2) * sizeof(double));
+  Rprintf("log(1) = %d\n", log(1));
   lgamma_arr[0] = 0;
   lgamma_arr[1] = 0;
+  Rprintf("log(1) = %d\n", log(1));
   for(int i = 2; i <= (n + 1); i = i + 1) {
 
+      Rprintf("computing lgamma at step %i\n", i);
+      Rprintf("lgamma_arr[i - 1] = %d\n", lgamma_arr[i - 1]);
+      Rprintf("log(i - 1) = %d\n", log(i - 1));
       lgamma_arr[i] = lgamma_arr[i - 1] + log(i - 1);
 
   }
+  Rprintf("log(1) = %d\n", log(1));
+  
+  Rprintf("lgamma_arr = [");
+  for(int i = 0; i <= (n + 1); i = i + 1) {
+    
+    Rprintf("%d, ", lgamma_arr[i]);
+    
+  }
+  Rprintf("]\n");
 
   b_vec_prev = (double *) malloc((n + 1) * sizeof(double));
   b_vec_prev[0] = pow((1 - b_vec[0]), n);
@@ -64,11 +80,20 @@ void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_poin
 
         b_vec_next[j] = b_vec_next[j] + exp(log(b_vec_prev[l]) + (j - l) * log(b_vec[k] -
           b_vec[k - 1]) + (n - j) * log(1 - b_vec[k]) - (n - l) * log(1 - b_vec[k - 1]) +
-          lgamma_arr[n - l + 1] - lgamma_arr[j - l + 1] - lgamma_arr[n - j + 1]);
+          lgamma(n - l + 1) - lgamma(j - l + 1) - lgamma(n - j + 1));
 
       }
 
     }
+    
+    Rprintf("k = %i\n", k);
+    Rprintf("b_vec_next = [", k);
[…]

### 2021-07-11 qqconf/src/jointlevel_two_sided.c
fixed overflow error and got rid of print statements

@@ -11,11 +11,9 @@
 // Parameter bound_id indicates if bound is upper or lower 
 void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *out) {
 
-  Rprintf("log(1) = %d\n", log(1));
   int n = *num_points;
   double *b_vec_prev;
   double *lgamma_arr;
-  Rprintf("log(1) = %d\n", log(1));
   // Pre-compute vector of lgamma values to avoid repeat computation
   lgamma_arr = (double *) malloc((n + 2) * sizeof(double));
   lgamma_arr[0] = 0;
@@ -25,8 +23,6 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
     lgamma_arr[i] = lgamma_arr[i - 1] + log(i - 1);
     
   }
-  
-  Rprintf("log(1) = %d\n", log(1));
   
   b_vec_prev = (double *) malloc((n + 1) * sizeof(double));
   b_vec_prev[0] = pow((1 - b_vec[0]), n);
@@ -68,7 +64,7 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
 
         b_vec_next[j] = b_vec_next[j] + exp(log(b_vec_prev[l]) + (j - l) * log(b_vec[k] -
           b_vec[k - 1]) + (n - j) * log(1 - b_vec[k]) - (n - l) * log(1 - b_vec[k - 1]) +
-          lgamma_arr[n - l + 1] - lgamma_arr[j - l + 1] - lgamma_arr[n - j + 1]);
+          lgamma(n - l + 1) - lgamma(j - l + 1) - lgamma(n - j + 1));
 
       }
 
@@ -79,7 +75,6 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
 
   }
 
-  Rprintf("log(1) = %d\n", log(1));
   *out = b_vec_prev[n];
   free(b_vec_prev);
   free(b_vec_next);

### 2021-07-11 qqconf/src/jointlevel_two_sided_ell_speedup.c

@@ -13,34 +13,18 @@
 // Uses speedup for equal local levels case 
 void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_points, double *out) {
 
-  Rprintf("log(1) = %d\n", log(1));
   int n = *num_points;
   double *b_vec_prev;
   double *lgamma_arr;
-  Rprintf("log(1) = %d\n", log(1));
   // Pre-compute vector of lgamma values to avoid repeat computation
   lgamma_arr = (double *) malloc((n + 2) * sizeof(double));
-  Rprintf("log(1) = %d\n", log(1));
   lgamma_arr[0] = 0;
   lgamma_arr[1] = 0;
-  Rprintf("log(1) = %d\n", log(1));
   for(int i = 2; i <= (n + 1); i = i + 1) {
 
-      Rprintf("computing lgamma at step %i\n", i);
-      Rprintf("lgamma_arr[i - 1] = %d\n", lgamma_arr[i - 1]);
-      Rprintf("log(i - 1) = %d\n", log(i - 1));
       lgamma_arr[i] = lgamma_arr[i - 1] + log(i - 1);
 
   }
-  Rprintf("log(1) = %d\n", log(1));
-  
-  Rprintf("lgamma_arr = [");
-  for(int i = 0; i <= (n + 1); i = i + 1) {
-    
-    Rprintf("%d, ", lgamma_arr[i]);
-    
-  }
-  Rprintf("]\n");
 
   b_vec_prev = (double *) malloc((n + 1) * sizeof(double));
   b_vec_prev[0] = pow((1 - b_vec[0]), n);
@@ -85,15 +69,6 @@ void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_poin
       }
 
     }
-    
-    Rprintf("k = %i\n", k);
-    Rprintf("b_vec_next = [", k);
-    for(int j = j_lower; j <= j_upper; j = j + 1) {
-      
-      Rprintf("%d, ", b_vec_next[j]);
-      
-    }
-    Rprintf("]\n");
 
     // Only copy over what is necessary
     if(k < n) memcpy(b_vec_prev + j_lower, b_vec_next + j_lower, (j_upper - j_lower + 1) * sizeof(double));
[…]

### 2021-07-11 qqconf/src/jointlevel_two_sided.c
made use of lgamma_arr

@@ -64,7 +64,7 @@ void jointlevel_twosided(double *b_vec, int *bound_id, int *num_points, double *
 
         b_vec_next[j] = b_vec_next[j] + exp(log(b_vec_prev[l]) + (j - l) * log(b_vec[k] -
           b_vec[k - 1]) + (n - j) * log(1 - b_vec[k]) - (n - l) * log(1 - b_vec[k - 1]) +
-          lgamma(n - l + 1) - lgamma(j - l + 1) - lgamma(n - j + 1));
+          lgamma_arr[n - l + 1] - lgamma_arr[j - l + 1] - lgamma_arr[n - j + 1]);
 
       }
 

### 2021-07-11 qqconf/src/jointlevel_two_sided_ell_speedup.c

@@ -64,7 +64,7 @@ void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_poin
 
         b_vec_next[j] = b_vec_next[j] + exp(log(b_vec_prev[l]) + (j - l) * log(b_vec[k] -
           b_vec[k - 1]) + (n - j) * log(1 - b_vec[k]) - (n - l) * log(1 - b_vec[k - 1]) +
-          lgamma(n - l + 1) - lgamma(j - l + 1) - lgamma(n - j + 1));
+          lgamma_arr[n - l + 1] - lgamma_arr[j - l + 1] - lgamma_arr[n - j + 1]);
 
       }
 
@@ -79,8 +79,8 @@ void jointlevel_twosided_ell_speedup(double *b_vec, int *bound_id, int *num_poin
 
   for(int l = l_lower; l <= l_upper; l = l + 1) {
 
-    *out = *out + exp(log(b_vec_prev[l]) + log(b_vec_next[n - l]) + lgamma(l + 1) + 
-      lgamma(n - l + 1) - lgamma(n + 1) - l * log(b_vec[n - 1]) - 
+    *out = *out + exp(log(b_vec_prev[l]) + log(b_vec_next[n - l]) + lgamma_arr[l + 1] + 
+      lgamma_arr[n - l + 1] - lgamma_arr[n + 1] - l * log(b_vec[n - 1]) - 
       (n - l) * log(1 - b_vec[n - 1]));
 
   }

### 2021-08-15 article/manuscript.tex
first cleanup of article

@@
 \newline
-First, we generate data to perform a regression. Here, we will generate each $\epsilon_{i}$ independently from a $t(2.5)$ distribution. 
-%
+First, we generate data to perform a regression. Here, we will generate each $\epsilon_{i}$ independently from a $t(3)$ distribution.
+
 \begin{Schunk}
 \begin{Sinput}
-R> set.seed(100)
+R> set.seed(20)
 R> n <- 100
 R> x <- runif(n)
-R> eta <- rt(n, df = 2.5)
+R> eta <- rt(n, df = 3)
 R> y <- x + eta
@@
 \end{Schunk}
-%
+
 Then, we fit a regression with the simulated data
-%
+
 \begin{Schunk}
@@
 \end{Schunk}
-%
+
 With \pkg{base}-\proglang{R} functionality, we can can create a qqplot using the function \code{qqnorm} and \code{qqline}.
-%
-%
+
 \begin{Schunk}
@@
 \end{Schunk}
+
+\begin{figure}
+\begin{center}
 \includegraphics{manuscript-base_qqplot}
-%
-%
-\newline
+\end{center}
+\caption{QQ Plot for Regression Residuals with Base R Functionality}
+\end{figure}
+
 Clearly there's some indication of deviation in this plot, but it can be hard to tell how significant the deviation is without confidence bounds.
 With our function \code{qq_conf_plot}, it is much easier to be able to judge the significance of the deviation.
-%
-%
+
 \begin{Schunk}
@@
 +    obs = reg$residuals,
-+    points_params = list(col="red")
++    points_params = list(col="blue", pch = 20, cex = .5)
 +  )
@@
 \end{Schunk}
+
+\begin{figure}
+\begin{center}
 \includegraphics{manuscript-qqconf_qqplot}
-%
-%
+\end{center}
+\caption{QQ Plot for Regression Residuals with ELL Bounds}
+\end{figure}
+
+Here, we can clearly see that both the left and right tail of the residuals goes beyond the normal testing bounds, giving strong evidence that the errors were not generated from a normal distribution.
 \newline
-Here, we can clearly see that in the right tail of the residuals goes beyond the normal testing bounds, giving strong evidence that the errors were not generated from a normal distribution.
+\newline
+This example also highlights an instance in which the ELL method is preferable to KS.
+Because KS is much more sensitive to deviations in the center of the distribution than it is to deviations in the tails of the distribution, it does not yeild a rejection of the null hypothesis in this case (Figure 7).
+We can generate KS bounds by simply setting the \code{method} arguments to \code{"ks"} in the \code{qq_conf_plot} function.
+
+\begin{Schunk}
+\begin{Sinput}
+R> library(qqconf)
+R> qq_conf_plot(
++    obs = reg$residuals,
++    method = "ks",
++    points_params = list(col="blue", pch = 20, cex = .5)
++  )
+\end{Sinput}
+\end{Schunk}
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-qqconf_qqplot_ks}
+\end{center}
+\caption{QQ Plot for Regression Residuals with KS Bounds}
+\end{figure}
 
 \subsection{Multiple Testing in Genome Wide Association Studies}
+\subsubsection{Applicability of Equal Local Levels to Genome Wide Association Studies}
 In genome wide association studies (GWAS), we are interested in identifying the genetic variants that are responsible for biological traits.
@@
 If a very specific distribution for $H_{A}$ is suspected, then it makes sense to use a test that has high power under this alternative, which may not be our local levels test.
-However, in the general case when little is known about the alternative distribution, using local levels is desirable because it is agnostic to alternative distributions.
-Moreover, since small p-values are often of great interest in GWAS because they can indicate the main biological drivers of a trait, the local levels test is far superior to the KS test due to its tail sensitivity.
-%Here is where the biological example goes with the code. I want to have the graphs that I make from this and then I also want
+However, in the general case when little is known about the alternative distribution, using local levels is desirable because it is agnostic to the space of alternative distributions.
+Moreover, since small p-values are often of great interest in GWAS because they can indicate the main biological drivers of a trait, the local levels test is far superior to the KS test due to its comparative tail sensitivity.
+\subsubsection{Appliction of Equal Local Levels to Creutzfeld-Jakob Disease}
+We downloaded the p-values from a GWAS of Creutzfeld-Jakob disease in a sample of 4110 cases and 13,569 controls \citep{jones2020identification}.
+Test of association between risk for the disease and genetic variants was done at 6,314,492 SNPs.
+Major genetic risk loci were found on chromosomes 1 and 20.
+Here, we remove those chromosomes from the results in order to display the p-values from tests that are not obviously from a non-uniform distribution.
+For display purposes, we subsample the remaining SNPs to 10,000 approximately evenly spaced SNPs.
+Subsampling helps ensure that correlations between SNPs that are located
+near each other is minimized.
+\begin{Schunk}
+\begin{Sinput}
+R> cjd_df <- read.table("data/cjd_sample.txt", header = TRUE)
+\end{Sinput}
+\end{Schunk}
+We then make QQ plots of these 10,000 tests with 95\% testing bands. First, we make a standard QQ plot of observed quantiles versus expected quantiles (Figure 8).
+\begin{Schunk}
+\begin{Sinput}
+R> library(qqconf)
+R> qq_conf_plot(
++    obs = cjd_df[,3],
++    distribution = qunif,
++    points_params = list(pch = 21, cex = 0.2)
++    )
+\end{Sinput}
+\end{Schunk}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.5]{manuscript-cjd_standard_qq}
+\end{center}
+\caption{Standard QQ Plot for CJD GWAS p-values}
+\end{figure}
+
+Unfortunately, this plot results in deviations from the expected line that are difficult to see.
+To aid visualization, we also plot the deviation of the observed quantiles from the expected quantiles versus the expected quantiles (Figure 9).
+This can be done easily by setting the \code{difference} parameter to \code{TRUE} in \code{qq_conf_plot}.
+\begin{Schunk}
+\begin{Sinput}
+R> qq_conf_plot(
++    obs = cjd_df[,3],
++    distribution = qunif,
++    points_params = list(pch = 21, cex = 0.2),
++    difference = TRUE
++    )
+\end{Sinput}
+\end{Schunk}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.5]{manuscript-cjd_diff_qq}
+\end{center}
+\caption{QQ Plot With y-axis as Observed - Expected Quantile for CJD GWAS p-values}
+\end{figure}
+
+This plot is much easier to interpret, but note that tests in which there is an association will result in small p-values, which will be difficult to see when the plot axes are on the 0 to 1 scale.
+To see the small p-values we repeat the plots but with the axes on the -log10 scale (Figures 10 and 11).
+This can be done by setting the \code{log10} parameter of \code{qqconf} to \code{TRUE}
+
+\begin{Schunk}
+\begin{Sinput}
+R> qq_conf_plot(
++    obs = cjd_df[,3],
++    distribution = qunif,
++    points_params = list(pch = 21, cex = 0.2),
++    log10 = TRUE
++    )
+\end{Sinput}
+\end{Schunk}
+
+\begin{figure}
+\begin{center}
+\includegraphics[scale=1.5]{manuscript-cjd_log_qq}
+\end{center}
+\caption{QQ Plot With y-axis as -$\textrm{log}_{10}$(Observed Quantile) for CJD GWAS p-values}
+\end{figure}
+
+\begin{Schunk}
+\begin{Sinput}
+R> qq_conf_plot(
++    obs = cjd_df[,3],
++    distribution = qunif,
++    points_params = list(pch = 21, cex = 0.2),
++    difference = TRUE,
++    log10 = TRUE,
++    ylim = c(-0.2, 1.1)
++    )
+\end{Sinput}
+\end{Schunk}
+
+\begin{figure}
+\begin{center}
+\includegraphics{manuscript-cjd_log_diff_qq}
+\end{center}
+\caption{QQ Plot With y-axis as -$\textrm{log}_{10}$(Observed Quantile) + $\textrm{log}_{10}$(Expected Quantile) for CJD GWAS p-values}
+\end{figure}
+
+From the QQ plots, we can see that there is an excess of small p-values, indicating that the test statistics do not follow the expected null distribution.
+
 \section{Discussion}
 \label{sec:discussion}
-The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for Q-Q plots.
+The local levels test using an exact recursive calculation allows for the creation of relatively fast and alternative-agnostic simultaneous testing bands for QQ plots.
 Of course, our method is limited by the assumptions that (1) all of the tests are independent and that (2) all of the parameters of the null distribution are known.
-Currently, we are not aware of methods to handle the dependent case that allow for bands on Q-Q plots.
-To handle the second issue, Aldor-Noiman has adapted their method such that it will yield exact results when some parameters of the null distribution are unknown.
-However, if the dataset is very large, Aldor-Noiman's method is prohibitively slow.
+Currently, we are not aware of methods to handle the dependent case that allow for bands on QQ plots.
+To handle the issue of parameter uncertainty, Aldor-Noiman has adapted their method such that it will yield exact results when some parameters of the null distribution are unknown.
+However, if the dataset is very large, Aldor-Noiman's method is prohibitively slow because it uses simulation.
 In this case, we suggest that our method be used because it is much faster, and with a sufficiently large dataset the uncertainty in the parameters will become negligible under standard regularity conditions.
-Methods to handle parameter uncertainty with an exact calculation have been discussed in the context of the normal distribution \citep{rosenkrantz2000confidence}, but a general method towards this end has not been developed, and would be an important next step.
+Methods to handle parameter uncertainty with an exact calculation (as opposed to simulation) have been discussed in the context of the normal distribution \citep{rosenkrantz2000confidence}, but a general method towards this end has not been developed, and would be an important next step.
 \newline

### 2021-08-16 qqconf/R/ppplot.R
updated code due to CRAN comments

@@ -51,6 +51,8 @@
 #' @param ... Additional parameters passed to the plot function.
 #' 
 #' @export
+#' 
+#' @return None, PP plot is produced.
 #'
 #' @examples
 #' set.seed(0)

### 2021-08-16 qqconf/R/qqplot.R

@@ -55,6 +55,8 @@
 #' @importFrom graphics abline lines plot points polygon
 #' 
 #' @export
+#' 
+#' @return None, QQ plot is produced.
 #'
 #' @examples
 #' set.seed(0)

### 2021-08-16 relative_error_calc.R
Delete relative_error_calc.R

@@ -1,39 +1,0 @@
-library(readr)
-library(dplyr)
-
-approx_table_df <- readr::read_csv(
-  "~/downloads/alpha_01_500k.csv"
-)
-
-# now, want to build a function that can do the approximation with the correction
-# this should be vectorizable
-
-# have to figure out what to feed in here as input
-get_approx <- function(alpha, n, c_alpha) {
-
-  eta_approx = -log(1-alpha)/(2*log(log(n))*log(n))*(1-c_alpha*log(log(log(n)))/log(log(n)))
-
-}
-
-approx_alphas <- get_approx(
-  alpha = .01,
-  n = approx_table_df$n,
-  c_alpha = 1.6
-)
-
-approx_table_df <- approx_table_df %>%
-  mutate(local_level_approx = approx_alphas)
-
-approx_table_df <- approx_table_df %>%
-  mutate(error = local_level_approx - local_level)
-
-approx_table_df <- approx_table_df %>%
-  mutate(relative_error = error / local_level)
-
-approx_table_df <- approx_table_df %>%
-  filter(n >= 1000)
-
-plot(approx_table_df$n, approx_table_df$relative_error, xlab = "n", ylab = expression(paste("Relative Error of ", eta[approx])))
-abline(h = 0)
-
-readr::write_csv(approx_table_df, "~/Documents/local_levels_relative_error.csv")

### 2021-08-16 plotting/qq_plots.R
Delete plotting directory

@@ -1,140 +1,0 @@
-##' QQ plot with global and pointwise confidence bounds
-##'
-##' Create a qq-plot with with a shaded global confidence interval and,
-##' optionally, lines for point-wise bounds. The observed values are plotted
-##' against their expected values had they come from the specified distribution.
-##'
-##' For $N$ independent tests that follow a specified distribution, the global
-##' confidence interval of size $C$ is the region such that the probability of
-##' all the points being in the region is $C$. The pointwise bounds are determined
-##' by taking the marginal probability that an individual point is within the bounds
-##' is $C$. If 'difference' is set to TRUE, the vertical axis plots the 
-##' observed quantile minus expected quantile. Set pw.lty to a non-zero line type to plot
-##' the pointwise bounds.
-##' 
-##' @param obs The observed data.
-##' @param dist The quantile distribution function, qunif by default.
-##' @param conf.int The size of the confidence interval for the expected quantiles.
-##' @param difference Whether to plot the difference between the observed and
-##'   expected values on the vertical axis.
-##' @param log10 Whether to plot axes on -log10 scale (e.g. to see small p-values).
-##' @param shade.col What color to use for the global confidence interval.
-##' @param add Whether to add points to an existing plot.
-##' @param dist.params List of additional parameters for the quantile distribution
-##'   function (e.g. df=1).
-##' @param bounds.params List of optional parameters for get_bounds_two_sided
-##'   (i.e. tol, max_it, method).
-##' @param pw.lty Line type for the pointwise error bounds. Set to non-zero for a line.
-##' @param pw.col Color for the pointwise bounds line.
-##' @param ... Additional parameters for the plot.
-##'
-##' @examples
-##' x <- rchisq(1000, 1)
-##' qq_conf_plot(x, qchisq, dist.params=list(df=1), pw.lty=3) # Plots x against a 1-df chisquare
-##'
-##' y <- runif(893)
-##' qq_conf_plot(y, difference = TRUE, log10 = TRUE, bounds.params = list(method = "search"), pch=3)
-qq_conf_plot <- function(obs,
-                         dist = qunif,
-                         conf.int = 0.95,
-                         difference = FALSE,
-                         log10 = FALSE,
-                         shade.col = 'gray',
[…]
